\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.35em,itemsep=0.3em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}
\newcommand{\Lang}{\mathcal{L}_{0}}
\newcommand{\LangPlus}{\mathcal{L}_{0}^{+H}}
\newcommand{\GenH}{\mathsf{Gen}_{H}}
\newcommand{\EqSrc}{\mathsf{Eq}_{\mathrm{src}}}
\newcommand{\RetainH}{\mathsf{Retain}_{H}}
\newcommand{\NoTargetH}{\mathsf{NoTarget}_{H}}
\newcommand{\NoTargetSyn}{\mathsf{NoTarget}_{H}^{\mathrm{syn}}}
\newcommand{\SrcTok}{\mathsf{Tok}_{0}}
\newcommand{\ForbidT}{\mathsf{Forbid}_{T}}
\newcommand{\ProxyT}{\mathsf{Proxy}_{T}}
\newcommand{\TraceH}{\mathsf{Trace}_{H}}
\newcommand{\Annot}{\mathsf{Ann}}
\newcommand{\Influence}{\mathsf{Infl}}
\newcommand{\FreezeH}{\mathsf{Freeze}_{H}}
\newcommand{\Pass}{\mathsf{Pass}}
\newcommand{\Fail}{\mathsf{Fail}}
\newcommand{\Block}{\mathsf{Block}}

\newtheorem{definitionblock}{Definition}
\newtheorem{criterion}{Criterion}
\newtheorem{finding}{Finding}
\newtheorem{obstruction}{Obstruction}
\newtheorem{verdict}{Local verdict}
\newtheorem{nextburden}{Next burden}

\title{\textbf{Localization Source-Basis Axiom Selector-Domain NoTarget Source-Freeze Inventory and Annotation/Influence Packet Attempt or Controlled Pause}\\[0.35em]
\large Registered-Source Check for the Missing NoTarget Source-Syntax Evidence Packet}
\author{Ontology Formalizer AgentJob AJ-RT-20260613-020-001}
\date{June 13, 2026}

\begin{document}

\maketitle

\begin{abstract}
This draft/control artifact attempts the next admissible step after the
\(\NoTargetSyn\) theorem attempt reached controlled pause: determine
whether the tracked record already supplies a source-registered frozen
inventory and annotation/influence packet for the trace under review. It
does not. The predecessor artifacts define the trace schema and the burden
vocabulary, but they do not supply a complete registered \(\SrcTok\)
inventory, an independently frozen \(\ForbidT\) inventory, a complete
\(\ProxyT\) inventory, checkable \(\Annot\) content, or complete
\(\Influence\) coverage. The correct local result remains controlled pause,
not \(\Pass\). \(\NoTargetH\), \(\NoTargetSyn\), \(\EqSrc\), \(\RetainH\),
and \(\GenH\) remain undischarged. Candidate reconstruction, canonical
ontology edit, benchmark promotion, Gate Chair review, and
completed-derivation language remain blocked.
\end{abstract}

\section{Scope}

This artifact is a draft/control output for task \texttt{RT-20260613-020}.
It is not a canonical ontology source and does not add source vocabulary to
\(\Lang\). It asks only whether the missing packet named by
\texttt{handoff-0036} is already available in tracked source authority.

The packet under review would need to supply:
\[
    \FreezeH^{\mathrm{src}} =
    (\SrcTok^{*},\ForbidT^{*},\ProxyT^{*},\Annot^{*},\Influence^{*})
\]
with source registration, scope, timing, and checkability sufficient for
the exact trace \(\TraceH=(E,R,Q,A,B,S)\). The asterisk denotes a packet
fixed for this local theorem path; it does not denote canonical adoption.

\section{Admissibility Criteria}

\begin{criterion}[Source-registered freeze packet]
A packet can move the branch past controlled pause only if all five
surfaces have explicit source-registration evidence:
\begin{enumerate}
    \item \(\SrcTok^{*}\) lists every token in \(E,R,Q,A,B,S\) or gives an
    explicit source-side introduction rule for each token.
    \item \(\ForbidT^{*}\) is frozen independently of benchmark outcome
    inspection and target-proxy inspection.
    \item \(\ProxyT^{*}\) classifies every candidate-performance proxy that
    can affect admission, equivalence, retention, ranking, status, or family
    selection.
    \item \(\Annot^{*}\) gives checkable source basis, timing, rule scope,
    and dependency content for every relevance, exclusion, quotient,
    retention, and status choice.
    \item \(\Influence^{*}\) gives complete syntactic edges into admission,
    equivalence, retention, ranking, status, and family selection, without a
    closed-world assumption that undeclared edges are false.
\end{enumerate}
\end{criterion}

\begin{criterion}[Conservative failure mode]
If any required surface is absent, incomplete, unfrozen, selected after
outcome inspection, circular, or target-equivalence dependent, the packet
cannot produce \(\Pass\). The branch remains \(\Block\) or controlled pause.
\end{criterion}

\section{Registered-Source Check}

The tracked predecessor artifacts provide a narrow evidence chain. The
repair-target packet defines the trace shape and burden vocabulary. The
Smuggling Auditor permits the repair target to move forward only as a
nonpromotional repair target. The theorem-attempt artifact confirms that
\(\NoTargetSyn\) is well formed as a local burden and then blocks because
the five freeze surfaces are not proved.

\begin{center}
\begin{tabular}{p{0.18\linewidth}p{0.36\linewidth}p{0.34\linewidth}}
\textbf{Surface} & \textbf{Tracked source evidence found} & \textbf{Local result} \\
\hline
\(\SrcTok^{*}\) & The repair target names a registered source-token inventory as required, but no predecessor artifact supplies a complete finite token table for \(E,R,Q,A,B,S\). & incomplete; \(\Block\) \\
\(\ForbidT^{*}\) & The repair target and audit name target metric behavior, target proper time, locality, observer protocol, benchmark label, target-favorable rank, and benchmark-success channels as forbidden. They do not prove independent pre-outcome freeze. & unfrozen; \(\Block\) \\
\(\ProxyT^{*}\) & Proxy risk is named and linked to admission, equivalence, retention, ranking, status, and family selection. No complete proxy inventory is registered. & incomplete; \(\Block\) \\
\(\Annot^{*}\) & Annotation is required for relevance and exclusion. No complete annotation table with source basis, timing, rule scope, and dependency content is supplied. & not checkable; \(\Block\) \\
\(\Influence^{*}\) & Influence destinations are named broadly. No complete edge ledger is supplied, and the audit forbids closed-world inference from missing edges. & incomplete; \(\Block\) \\
\end{tabular}
\end{center}

\section{Obstructions}

\begin{obstruction}[Burden vocabulary is not the burden evidence]
The predecessor artifacts correctly name \(\SrcTok\), \(\ForbidT\),
\(\ProxyT\), \(\Annot\), and \(\Influence\). Naming these surfaces defines
what must be checked; it does not supply the inventories, annotations, or
edge ledger required to pass the check.
\end{obstruction}

\begin{obstruction}[The current packet is not an independent prefreeze]
This artifact is authored after the \(\NoTargetSyn\) theorem attempt reached
controlled pause. It can record the absence of sufficient frozen authority,
but it cannot retroactively prove that \(\ForbidT^{*}\) or \(\ProxyT^{*}\)
was fixed before outcome or proxy inspection for the trace under review.
\end{obstruction}

\begin{obstruction}[No closed-world completion is available]
The influence surface explicitly blocks a closed-world default. Therefore
the absence of a listed proxy or influence edge is not evidence that the
proxy or edge is absent. It is evidence that the branch remains
underdetermined.
\end{obstruction}

\section{Partial Packet Ledger}

The strongest source-faithful packet available from the tracked record is
therefore a partial packet:
\[
    \FreezeH^{\mathrm{partial}} =
    (\SrcTok^{?},\ForbidT^{?},\ProxyT^{?},\Annot^{?},\Influence^{?}),
\]
where the question mark marks missing completeness or missing independent
freeze evidence. This partial packet is useful as a diagnostic ledger, but
it is not sufficient theorem evidence.

\begin{finding}[What the partial packet preserves]
The partial packet preserves three useful constraints:
\begin{enumerate}
    \item direct target channels are treated as forbidden channels rather
    than source primitives;
    \item unclassified proxy and influence surfaces remain blockers rather
    than being silently ignored; and
    \item source-side annotations must become checkable records rather than
    authority labels.
\end{enumerate}
\end{finding}

\begin{finding}[What the partial packet does not prove]
The partial packet does not prove source-token completeness, independent
forbidden-token freeze, proxy completeness, annotation checkability, or
influence coverage. It therefore cannot discharge \(\NoTargetSyn\), and it
cannot serve as input to \(\EqSrc\), \(\RetainH\), or \(\GenH\) discharge.
\end{finding}

\section{Local Verdict}

\begin{verdict}[Source-freeze packet attempt reaches controlled pause]
The tracked record does not yet supply the source-registered frozen
inventory and annotation/influence packet required by \texttt{handoff-0036}.
The local value remains
\[
    \NoTargetSyn(\TraceH;\FreezeH^{\mathrm{partial}})=\Block,
\]
not \(\Pass\).
\end{verdict}

\begin{verdict}[No downstream discharge follows]
This controlled pause does not prove \(\NoTargetH\) or \(\NoTargetSyn\),
does not discharge \(\EqSrc\), \(\RetainH\), or \(\GenH\), and does not
provide candidate-ready source-basis evidence. Candidate reconstruction,
canonical ontology edit, benchmark promotion, Gate Chair review, and
completed-derivation language remain blocked.
\end{verdict}

\section{Next Burden}

\begin{nextburden}[Independent freeze manifest required]
The logical next step is to preserve the controlled pause unless a future
bounded task supplies an independently source-registered freeze manifest.
That manifest must include object identifiers, source paths, hashes or
equivalent immutability witnesses, scope statements, timing statements, a
complete token table, a complete forbidden-token table, a complete proxy
table, a checkable annotation table, and a complete influence-edge ledger
for the exact trace under review. Even such a manifest would remain
draft/control authority unless separately authorized.
\end{nextburden}

\section*{References}

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain NoTarget source-syntax theorem attempt or controlled pause:
Frozen provenance test for source tokens, forbidden tokens, proxies,
annotations, and influence} [Unpublished manuscript]. The Aether-Flow
Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-019/artifacts/35\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_SYNTAX\_THEOREM\_ATTEMPT\_OR\_CONTROLLED\_PAUSE.tex}.

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain NoTarget source-syntax repair-target smuggling audit:
Hidden target import, proxy selection, annotation, influence, and authority
review} [Unpublished manuscript]. The Aether-Flow Interpretation of
Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-018/artifacts/34\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_SYNTAX\_REPAIR\_TARGET\_SMUGGLING\_AUDIT.tex}.

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain NoTarget source-syntax repair-target packet: Least-broad
mechanization target for target-exclusion syntax} [Unpublished manuscript].
The Aether-Flow Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-017/artifacts/33\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_SYNTAX\_REPAIR\_TARGET\_PACKET.tex}.

\end{document}
