\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.35em,itemsep=0.3em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}
\newcommand{\Lang}{\mathcal{L}_{0}}
\newcommand{\PackFam}{\mathfrak{P}}
\newcommand{\EnumFam}{\mathfrak{E}}
\newcommand{\CertFam}{\mathfrak{C}}
\newcommand{\OutFam}{\mathfrak{O}}
\newcommand{\LedgerFam}{\mathfrak{H}}
\newcommand{\MetaG}{\mathfrak{G}}
\newcommand{\Ad}{\mathsf{Ad}}
\newcommand{\Blind}{\mathsf{Blind}}
\newcommand{\Force}{\mathsf{Force}}
\newcommand{\Status}{\mathsf{Status}}
\newcommand{\Neg}{\mathsf{Neg}}
\newcommand{\Pass}{\mathsf{Pass}}
\newcommand{\Block}{\mathsf{Block}}
\newcommand{\Pause}{\mathsf{Pause}}

\newtheorem{auditfinding}{Audit finding}
\newtheorem{risk}{Residual risk}
\newtheorem{auditverdict}{Audit verdict}
\newtheorem{nextburden}{Next burden}

\title{\textbf{Localization Source-Basis Axiom Selector-Domain Source-Forcing Smuggling Audit}\\[0.35em]
\large Target-Import and Authority-Expansion Review of the Obligation Packet}
\author{Smuggling Auditor AgentJob AJ-RT-20260613-005-001}
\date{June 13, 2026}

\begin{document}

\maketitle

\begin{abstract}
This draft/control audit reviews the selector-domain source-forcing
obligation packet for hidden target import and protected authority expansion.
The packet passes a narrow declaration screen: it does not adopt target metric,
target proper-time, target observer, target rank, target locality, or
benchmark-success predicates as source primitives. However, it is not
candidate-ready. Each source-forcing obligation remains a theorem-discharge
burden, and several burdens can be discharged only by either source-side
theorem evidence already expressible in the registered source language or a
future human-gated authority expansion. The audit therefore preserves a
controlled pause. It does not authorize candidate reconstruction, canonical
ontology edits, benchmark promotion, Gate Chair review, or any claim that an
effective relativistic sector has been derived.
\end{abstract}

\section{Scope}

This artifact is a draft/control output for task \texttt{RT-20260613-005}.
It audits
\texttt{24\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_SOURCE\_FORCING\_OBLIGATION\_PACKET.tex}.
The audit target is not whether the obligations are true. The target is
narrower: whether the obligations themselves smuggle target structure or
silently require protected authority expansion before they can be used as
candidate support.

The relevant source-forcing standard says that a choice surface \(X\) is
candidate-usable only if a source-side rule
\[
    \Force_X:\Lang \longrightarrow X
\]
and a theorem obligation collapse every \(\Ad\)-admissible and
\(\Blind\)-blind alternative to source equivalence, source impossibility, or
negative-control retention. This audit asks whether that standard is still a
source-side standard after it is applied to ledgers, horizons, grammars,
certificates, output bases, and \(D_F\) status transitions.

\section{Audit Method}

For each obligation surface, the audit checks four channels:

\begin{enumerate}
    \item \textbf{Direct target primitive import}: target metric, target
    proper-time, target observer protocol, target locality, target rank, or
    benchmark success used as a source primitive.
    \item \textbf{Selection import}: an apparently invariant singleton created
    by choosing a favorable ledger, horizon, grammar, certificate, output
    basis, or status threshold from a larger admissible family.
    \item \textbf{Omission import}: adverse source-definable alternatives
    removed by relevance labels, convenience, or non-computation rather than a
    source theorem.
    \item \textbf{Protected authority expansion}: a proof burden that cannot
    be stated or discharged without canonical ontology authority, benchmark
    status authority, Gate Chair authority, or permanent role registration.
\end{enumerate}

\section{Ledger Provenance}

\begin{auditfinding}[No direct ledger target primitive]
The ledger-provenance obligation explicitly forbids target metric behavior,
target locality, target observer protocols, target proper-time normalization,
target-favorable rank, and benchmark-success predicates as evidence that a
ledger \(H\) is the correct ledger. As a declaration, this is target-clean.
\end{auditfinding}

\begin{risk}[Ledger closure is still authority-sensitive]
The provenance object
\[
\Pi_H=(\mathcal{R}_{0},\mathcal{C}_{0},\mathcal{O}_{0},
\mathcal{Q}_{0},\mathcal{B}_{0})
\]
is safe only if all five components are already registered source records,
source closure rules, source operation seeds, source quotient seeds, and
pre-benchmark blinding records. If any component must be introduced as new
canonical ontology, the discharge path becomes a protected authority
expansion. If any component is selected because it reproduces the target
benchmark, the discharge path becomes a hidden target import.
\end{risk}

\section{Horizon Universality}

\begin{auditfinding}[Horizon obligation names the correct risk]
The horizon-universality obligation rejects fixed favorable horizons and asks
for a source-generated family \(\mathcal{B}_{\mathrm{src}}\) with monotone
saturation. This directly addresses the earlier finite-variation failure
mode.
\end{auditfinding}

\begin{risk}[Universal horizon coverage is not yet source-forced]
The packet does not prove that \(\mathcal{B}_{\mathrm{src}}\) covers every
admissible horizon or that excluded horizons are impossible by source theorem.
Until such coverage exists, a horizon cutoff can still hide target locality,
target scale, or target-success selection. The safe status is
\(\mathsf{not\_computed}\), \(\mathsf{underdetermined}\), or
\(\mathsf{family\_valued}\), not \(\mathsf{invariant}\).
\end{risk}

\section{Admissibility Meta-Grammar}

\begin{auditfinding}[Meta-grammar requirement is target-clean as stated]
The meta-grammar obligation requires the enumerator families \(\EnumFam_i\) to
generate narrower, broader, and incomparable source-admissible grammars from
the same source seeds. It also requires omitted grammars to receive source-side
labels. These constraints are aligned with target-import prevention.
\end{auditfinding}

\begin{risk}[Completeness over grammars is the main smuggling channel]
The obligation remains vulnerable if the grammar family is declared complete
without a source theorem. In particular, the labels
\(\mathsf{source\_invalid}\) and \(\mathsf{authority\_expansion}\) can become
opaque rejection bins unless they preserve the exact source rule, failure
condition, and missing authority. A target-favorable grammar family selected
after seeing benchmark behavior would fail this audit.
\end{risk}

\section{Certificate Invariance}

\begin{auditfinding}[Replay is correctly separated from invariance]
The obligation packet correctly says that replayability is not certificate
invariance. It requires either equality across admissible certificate rules or
negative-control retention of certificate-sensitive outputs. This is a
necessary anti-smuggling constraint.
\end{auditfinding}

\begin{risk}[Kept and omitted cases remain theorem burdens]
No certificate family \(\CertFam_i\) is proven complete here. Therefore a
future discharge must show that every kept and omitted certificate rule is
covered by the invariance theorem or retained as adverse evidence. Any
certificate exclusion justified by target irrelevance, target success, or
candidate convenience would import the target.
\end{risk}

\section{Output-Basis Generation}

\begin{auditfinding}[Adverse-retaining output basis blocks favorable projection]
The output-basis obligation requires a source-side generator
\[
\mathsf{Gen}_{O,i}:\Lang\times \EnumFam_i\times\CertFam_i
\longrightarrow \OutFam_i
\]
and requires favorable, adverse, and neutral quantities at the same grain. As
a declaration, this blocks the most direct favorable-projection channel.
\end{auditfinding}

\begin{risk}[Output vocabulary may require source-language expansion]
The listed outputs include presentation boundaries, support fronts,
discriminator ranks, quotient spectra, transport cycles, holonomy reports, and
status rows. These objects are acceptable only if they are source-definable in
the registered language or tracked as explicit source-extension hypotheses. If
their definitions are imported from the target effective geometry, the output
basis smuggles target structure. If their source definitions require canonical
ontology extension, that extension is protected and cannot be granted by this
audit.
\end{risk}

\section{\texorpdfstring{\(D_F\)}{DF} Status Transitions}

\begin{auditfinding}[Invariant status is properly blocked by missing theorem evidence]
The obligation packet requires ledger provenance, horizon universality,
meta-grammar completeness, certificate invariance, output-basis completeness,
and independent target-import audit before a transition into
\(\mathsf{invariant}\). This is a correct non-promotional guard.
\end{auditfinding}

\begin{risk}[Independent audit cannot substitute for theorem discharge]
This audit can check target-import and authority-expansion channels. It cannot
prove the six theorem obligations. Therefore \(D_F\) may not transition to
\(\mathsf{invariant}\) on the basis of this audit alone. The status remains
blocked unless later source-side theorem evidence is registered and survives
the same anti-selection constraints.
\end{risk}

\section{Authority-Expansion Ledger}

\begin{center}
\begin{tabular}{p{0.2\linewidth}p{0.38\linewidth}p{0.29\linewidth}}
\textbf{Surface} & \textbf{Audit result} & \textbf{Blocked expansion channel} \\
\hline
Ledger provenance & no direct target primitive; theorem not discharged &
new canonical provenance rules or benchmark-selected ledger seeds \\
Horizon family & correct universality burden; coverage not proved &
target scale, target locality, or favorable finite cutoff \\
Meta-grammar & target-clean declaration; completeness not proved &
opaque omission labels or grammar family selected by benchmark success \\
Certificates & replay and invariance separated; families incomplete &
certificate exclusions based on target relevance or candidate convenience \\
Output bases & adverse-retaining generator required; definitions pending &
target-derived rank, front, spectrum, transport, or holonomy vocabulary \\
\(D_F\) & invariant transition correctly guarded; no theorem discharge &
audit used as substitute for source-forcing theorem evidence \\
\end{tabular}
\end{center}

\section{Local Verdict}

\begin{auditverdict}[Declaration screen passed; promotion remains blocked]
The source-forcing obligation packet passes a narrow target-import declaration
screen. It does not directly adopt target metric, target proper-time, target
observer, target rank, target locality, or benchmark-success evidence as a
source primitive. It also correctly names authority expansion as a possible
pause condition.
\end{auditverdict}

\begin{auditverdict}[Controlled pause preserved]
The packet is not candidate-ready. Its obligations are theorem burdens, not
theorem discharges. Candidate reconstruction remains blocked until each burden
is either discharged by registered source-side theorem evidence, retained as a
negative-control family, or explicitly routed to a human-gated authority
expansion. A Refuter benchmark-independence test is premature until there is a
source-side discharge protocol or a specific controlled-pause ledger to test.
\end{auditverdict}

This verdict is local and non-promotional. It does not modify canonical
ontology, promote benchmark status, issue a Gate Chair verdict, authorize
candidate reconstruction, or reject the \TheoryProgram{} globally.

\section{Next Burden}

\begin{nextburden}[Discharge protocol or controlled-pause ledger]
The logical next role is an Ontology Formalizer AgentJob that writes a
source-forcing discharge protocol or controlled-pause ledger. That artifact
should distinguish, for each of the six surfaces, between:
\begin{enumerate}
    \item source-side theorem obligations expressible in the current
    registered language;
    \item negative-control families that must be retained rather than
    projected away;
    \item obligations requiring protected authority expansion; and
    \item obligations that remain \(\mathsf{not\_computed}\) or
    \(\mathsf{underdetermined}\).
\end{enumerate}
It must not authorize candidate reconstruction, canonical ontology edit,
benchmark promotion, or Gate Chair review.
\end{nextburden}

\section*{References}

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain source-forcing obligation packet: Ledger, horizon, grammar,
certificate, output-basis, and \(D_F\) transition burdens} [Unpublished
manuscript]. The Aether-Flow Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-004/artifacts/24\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_SOURCE\_FORCING\_OBLIGATION\_PACKET.tex}.

Ricciardi, A. S. (2026, June 11). \emph{Localization source-basis axiom
selector-domain finite-variation benchmark-independence refutation:
Stability test for ledger, packet, horizon, enumerator, certificate,
output-basis, and \(D_F\) gate variation} [Unpublished manuscript]. The
Aether-Flow Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260611-006/artifacts/23\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_FINITE\_VARIATION\_BENCHMARK\_INDEPENDENCE\_REFUTATION.tex}.

Ricciardi, A. S. (2026, June 10). \emph{Localization source-basis axiom
selector-domain finite-variation smuggling audit: Target-import review of
family generators, horizons, certificates, output bases, and status gates}
[Unpublished manuscript]. The Aether-Flow Interpretation of Relativity
Research Project,
\texttt{research\_control/tasks/RT-20260608-023/artifacts/22\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_FINITE\_VARIATION\_SMUGGLING\_AUDIT.tex}.

\end{document}
