\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.35em,itemsep=0.3em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}
\newcommand{\Lang}{\mathcal{L}_{0}}
\newcommand{\LedgerFam}{\mathfrak{H}}
\newcommand{\Ad}{\mathsf{Ad}}
\newcommand{\Blind}{\mathsf{Blind}}
\newcommand{\ForceH}{\mathsf{Force}_{H}}
\newcommand{\LedgerProv}{\mathsf{LedgerProv}}
\newcommand{\Gen}{\mathsf{Gen}}
\newcommand{\EqSrc}{\mathsf{Eq}_{\mathrm{src}}}
\newcommand{\Neg}{\mathsf{Neg}}
\newcommand{\Expand}{\mathsf{Expand}}
\newcommand{\Unres}{\mathsf{Unresolved}}
\newcommand{\Pause}{\mathsf{Pause}}
\newcommand{\Current}{\mathsf{Current}}

\newtheorem{definitionblock}{Definition}
\newtheorem{attempt}{Theorem attempt}
\newtheorem{lemma}{Lemma}
\newtheorem{obstruction}{Obstruction}
\newtheorem{pauserule}{Controlled-pause rule}
\newtheorem{localverdict}{Local verdict}
\newtheorem{nextburden}{Next burden}

\title{\textbf{Localization Source-Basis Axiom Selector-Domain Ledger-Provenance Theorem Attempt or Controlled Pause}\\[0.35em]
\large Single-Surface Current-Language Test for \(\Pi_H\), \(H\), and Admissible Ledger Retention}
\author{Ontology Formalizer AgentJob AJ-RT-20260613-009-001}
\date{June 13, 2026}

\begin{document}

\maketitle

\begin{abstract}
This draft/control artifact attempts exactly one source-forcing theorem
surface: ledger provenance \(H\). It states the current-language theorem
form
\[
\LedgerProv_{\Lang}(\Pi_H,H,\LedgerFam)
\]
for
\[
\Pi_H=(\mathcal{R}_{0},\mathcal{C}_{0},\mathcal{O}_{0},
\mathcal{Q}_{0},\mathcal{B}_{0})
\]
and tests whether \(\Pi_H\) is generated inside the registered source
language \(\Lang\), whether \(H\) is unique up to source relabeling, or
whether every non-equivalent admissible ledger can be completely retained as
a negative-control alternative. The theorem is well-formed as a burden, but
the proof is not discharged: the current registered source language does
not provide a source-forced ledger generator, a uniqueness theorem, or a
complete admissible-ledger inventory. The result is a controlled pause for
ledger provenance. Candidate reconstruction, canonical ontology edit,
benchmark promotion, Gate Chair review, and completed-derivation language
remain blocked.
\end{abstract}

\section{Scope}

This artifact is a draft/control output for task \texttt{RT-20260613-009}.
It responds to the benchmark-independence refutation's next burden: isolate
the least broad constructive surface, ledger provenance \(H\), and attempt
one current-language theorem or stop cleanly.

The scope is deliberately single-surface. Horizon universality,
admissibility meta-grammar completeness, certificate invariance,
output-basis generation, and \(D_F\) status transitions are not solved here.
They remain dependent surfaces. This artifact does not edit canonical
ontology TeX, adopt A0--A4 or selection laws as canonical ontology,
authorize candidate reconstruction, issue a Gate Chair verdict, promote
benchmark status, or reject the broader \TheoryProgram{}.

\section{Theorem Form}

\begin{definitionblock}[Ledger-provenance theorem target]
Let \(\Lang\) denote the registered source language before the A0--A4
extension sequence. Let \(H\) be the ledger surface and let
\[
\Pi_H=(\mathcal{R}_{0},\mathcal{C}_{0},\mathcal{O}_{0},
\mathcal{Q}_{0},\mathcal{B}_{0})
\]
collect registered source records, source closure rules, source operation
seeds, source quotient seeds, and pre-benchmark blinding records.
The desired theorem is
\[
\LedgerProv_{\Lang}(\Pi_H,H,\LedgerFam),
\]
meaning:
\begin{enumerate}
    \item each component of \(\Pi_H\) is definable in \(\Lang\);
    \item there is a source-side generator
    \[
    \ForceH:\Lang\longrightarrow (H,\LedgerFam)
    \]
    whose input does not include target metric behavior, target locality,
    target observer protocol, target proper-time normalization,
    target-favorable rank, or benchmark-success predicates;
    \item every \(\Ad\)-admissible and \(\Blind\)-blind ledger \(H'\)
    generated from the same provenance class is either equivalent to \(H\)
    under explicitly declared source relabeling, source-impossible in
    \(\Lang\), or retained in \(\LedgerFam\) as a negative control whose
    outputs cannot be projected into candidate support.
\end{enumerate}
\end{definitionblock}

\begin{attempt}[Single-surface theorem attempt]
Prove
\[
\LedgerProv_{\Lang}(\Pi_H,H,\LedgerFam).
\]
Equivalently, establish one of the following outcomes:
\begin{enumerate}
    \item \textbf{Generated and unique:} \(\Pi_H\) is definable in
    \(\Lang\), \(\ForceH\) generates \(H\), and every admissible blind
    ledger \(H'\) is source-equivalent to \(H\).
    \item \textbf{Generated but non-unique with complete retention:}
    \(\Pi_H\) is definable in \(\Lang\), multiple admissible ledgers exist,
    and all non-equivalent ledgers are enumerated or schema-retained in
    \(\LedgerFam\) without projection into candidate support.
    \item \textbf{Controlled pause:} generation, uniqueness, or complete
    retention cannot be proved without target import, new canonical
    ontology authority, or an incomplete admissible-family inventory.
\end{enumerate}
\end{attempt}

\section{Component Inventory}

The current source-control chain gives a precise obligation for each
component of \(\Pi_H\), but it does not yet provide the required theorem.

\begin{center}
\begin{tabular}{p{0.16\linewidth}p{0.37\linewidth}p{0.31\linewidth}}
\textbf{Component} & \textbf{Required source-language content} & \textbf{Current result} \\
\hline
\(\mathcal{R}_{0}\) & registered source records used to generate ledger entries & named as required provenance, not proved complete \\
\(\mathcal{C}_{0}\) & source closure rules determining admissible ledger breadth & named as required provenance, not proved unique \\
\(\mathcal{O}_{0}\) & source operation seeds determining allowed ledger operations & named as required provenance, not proved exhaustive \\
\(\mathcal{Q}_{0}\) & source quotient seeds determining source relabeling and equivalence & named as required provenance, not proved complete \\
\(\mathcal{B}_{0}\) & pre-benchmark blinding records and hashes & valid provenance evidence, not source-necessity evidence \\
\end{tabular}
\end{center}

\begin{lemma}[Well-formed burden]
The theorem target is well-formed as a current-language burden. Prior
control artifacts define the allowed content of \(\Pi_H\), the forbidden
target evidence, and the acceptable outcomes of uniqueness, complete
negative-control retention, or controlled pause.
\end{lemma}

\begin{proof}
The source-forcing obligation packet states that \(H\) must be generated
from \(\Pi_H\) using only registered source records, source closure rules,
source operation seeds, source quotient seeds, and pre-benchmark blinding
records. The discharge protocol then places this requirement in
\(\Current_H\), broader or incomparable source ledgers in \(\Neg_H\), new
provenance authority in \(\Expand_H\), and absent proof or incomplete
retention in \(\Unres_H\). The benchmark-independence refutation identifies
ledger provenance as the least broad constructive burden. Therefore the
statement of \(\LedgerProv_{\Lang}(\Pi_H,H,\LedgerFam)\) is syntactically
and procedurally authorized as a draft/control theorem attempt.
\end{proof}

\section{Proof Attempt}

The proof would require four steps:

\begin{enumerate}
    \item \textbf{Definability:} define every component of \(\Pi_H\) inside
    \(\Lang\) without importing target metric behavior, target locality,
    target observer protocols, target proper-time normalization,
    target-favorable rank, or benchmark-success predicates.
    \item \textbf{Generation:} define \(\ForceH:\Lang\to(H,\LedgerFam)\)
    so that \(H=\ForceH(\Lang)\) or \(H\) is the distinguished member of the
    generated ledger family by a source rule.
    \item \textbf{Uniqueness:} prove that every admissible blind ledger
    \(H'\) generated from the same provenance class satisfies
    \(\EqSrc(H',H)\).
    \item \textbf{Retention fallback:} if uniqueness fails, prove that the
    full non-equivalent family is enumerated or schema-retained in
    \(\LedgerFam\), and that no retained alternative is projected into
    candidate support.
\end{enumerate}

The available tracked artifacts complete the statement of steps 1--4 as
obligations. They do not complete the proof of steps 2--4.

\begin{obstruction}[No source-forced ledger generator]
The current registered source language does not provide a theorem selecting
a unique source-side generator \(\ForceH\). The available records specify
what such a generator may use, but they do not derive the generator itself
from \(\Lang\).
\end{obstruction}

This obstruction blocks the generated-and-unique outcome. Naming
\(\mathcal{R}_{0}\), \(\mathcal{C}_{0}\), \(\mathcal{O}_{0}\),
\(\mathcal{Q}_{0}\), and \(\mathcal{B}_{0}\) as allowed provenance is not
the same as proving that those components force \(H\).

\begin{obstruction}[No uniqueness theorem]
The current record does not prove that all \(\Ad\)-admissible and
\(\Blind\)-blind ledgers generated from the same provenance class are
equivalent to \(H\) up to declared source relabeling. Broader, narrower, and
incomparable closure and quotient rules remain live alternatives.
\end{obstruction}

This obstruction blocks the uniqueness branch. A target-clean ledger can
still be non-unique under admissible source-side variation.

\begin{obstruction}[No complete admissible-ledger inventory]
The current record does not enumerate or schema-retain every non-equivalent
admissible ledger in \(\LedgerFam\). It identifies the retention obligation,
but it does not prove that the retained family is complete.
\end{obstruction}

This obstruction blocks the generated-but-non-unique branch. Without a
complete inventory, dependent rows cannot move into candidate support.

\section{Forbidden Evidence Check}

No part of this theorem attempt uses target metric behavior, target
locality, target observer protocols, target proper-time normalization,
target-favorable rank, or benchmark-success predicates as ledger evidence.
That restraint is necessary but not sufficient. Passing the forbidden-
evidence screen establishes target cleanliness of the attempt; it does not
establish source generation, uniqueness, or complete retention.

\section{Controlled-Pause Packet}

\begin{pauserule}[Ledger-provenance pause]
The ledger-provenance surface \(H\) must remain in controlled pause for
candidate-support purposes because:
\begin{enumerate}
    \item \(\ForceH\) is not derived inside \(\Lang\);
    \item uniqueness of \(H\) up to declared source relabeling is not
    proved;
    \item complete enumeration or schema-retention of non-equivalent
    admissible ledgers is not proved; and
    \item adding a primitive, rule, or authority to close those gaps would
    be protected expansion rather than local theorem discharge.
\end{enumerate}
\end{pauserule}

The pause is local. It does not reject the \TheoryProgram{} and does not
forbid later source-side theorem work. It prevents this ledger surface from
being used as candidate support before a source-language generator,
uniqueness theorem, or complete negative-control retention theorem exists.

\section{Decision Ledger}

\begin{center}
\begin{tabular}{p{0.28\linewidth}p{0.42\linewidth}p{0.18\linewidth}}
\textbf{Question} & \textbf{Finding} & \textbf{Status} \\
\hline
Is the theorem form authorized? & Yes. It is a draft/control theorem burden inherited from the source-forcing packet and refutation. & stated \\
Is \(\Pi_H\) fully generated inside \(\Lang\)? & Not proved. The current record names admissible provenance classes but does not derive \(\ForceH\). & unresolved \\
Is \(H\) unique up to source relabeling? & Not proved. Broader, narrower, and incomparable closure and quotient alternatives remain possible. & unresolved \\
Are all alternatives completely retained? & Not proved. The retention obligation is stated, but completeness of \(\LedgerFam\) is not established. & unresolved \\
Can candidate reconstruction proceed? & No. Ledger provenance remains controlled-pause evidence only. & blocked \\
\end{tabular}
\end{center}

\section{Local Verdict}

\begin{localverdict}[Theorem attempt reaches controlled pause]
The single-surface theorem attempt is well-formed but not discharged. The
current registered source language and tracked control artifacts do not
prove ledger generation, ledger uniqueness, or complete admissible-ledger
retention for \(H\). The correct result is a controlled-pause packet, not a
candidate-construction prelude and not a general repair packet.
\end{localverdict}

Candidate reconstruction, canonical ontology edit, benchmark promotion,
Gate Chair review, and completed-derivation claims remain blocked.

\section{Next Burden}

\begin{nextburden}[Stop locally unless expansion is explicitly authorized]
The logical next step is to preserve the ledger-provenance controlled pause.
An autonomous Candidate Constructor step is not authorized. A local
Smuggling Auditor cannot turn the pause into theorem evidence, because the
missing object is not an audit verdict but a source-language generator,
uniqueness theorem, or complete negative-control inventory. If the project
chooses to continue this branch, the next move must be explicitly
human-authorized ontology-expansion analysis for the missing ledger-
generation authority, or else the branch should remain paused as a negative
control.
\end{nextburden}

\section*{References}

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain source-forcing discharge protocol benchmark-independence
refutation: Stability test for four-cell ledger classification under
source-side variation} [Unpublished manuscript]. The Aether-Flow
Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-008/artifacts/28\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_SOURCE\_FORCING\_DISCHARGE\_PROTOCOL\_BENCHMARK\_INDEPENDENCE\_REFUTATION.tex}.

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain source-forcing discharge protocol: Current-language
obligations, negative controls, protected expansions, and unresolved
statuses} [Unpublished manuscript]. The Aether-Flow Interpretation of
Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-006/artifacts/26\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_SOURCE\_FORCING\_DISCHARGE\_PROTOCOL.tex}.

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain source-forcing obligation packet: Ledger, horizon, grammar,
certificate, output-basis, and \(D_F\) transition burdens} [Unpublished
manuscript]. The Aether-Flow Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-004/artifacts/24\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_SOURCE\_FORCING\_OBLIGATION\_PACKET.tex}.

\end{document}
