\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.35em,itemsep=0.3em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}
\newcommand{\Lang}{\mathcal{L}_{0}}
\newcommand{\Pack}{\mathcal{P}}
\newcommand{\PackFam}{\mathfrak{P}}
\newcommand{\EnumFam}{\mathfrak{E}}
\newcommand{\Cert}{\mathsf{Cert}}
\newcommand{\OutFam}{\mathfrak{O}}
\newcommand{\Ledger}{\mathsf{Ledger}}
\newcommand{\Rel}{\mathsf{Rel}}
\newcommand{\GammaB}{\Gamma}
\newcommand{\Ad}{\mathsf{Ad}}
\newcommand{\Blind}{\mathsf{Blind}}

\newtheorem{auditfinding}{Audit finding}
\newtheorem{smugglingrisk}{Smuggling risk}
\newtheorem{promotionblocker}{Promotion blocker}
\newtheorem{auditverdict}{Audit verdict}
\newtheorem{nextburden}{Next burden}

\title{\textbf{Localization Source-Basis Axiom Selector-Domain Finite-Variation Smuggling Audit}\\[0.35em]
\large Target-Import Review of Family Generators, Horizons, Certificates, Output Bases, and Status Gates}
\author{Smuggling Auditor AgentJob AJ-RT-20260608-023-001}
\date{June 10, 2026}

\begin{document}

\maketitle

\begin{abstract}
This draft audits the selector-domain finite-variation repair packet for
hidden target import. The repair packet is a real control improvement: it
replaces a single sealed survey path with explicit benchmark-blind packet
families, enumerator-family completeness obligations, typed certificate
exclusion ledgers, output-map stability criteria, and \(D_F\) evidence gates.
It passes a narrow declaration screen because it continues to forbid direct
target metric, null-cone, coordinate, observer-protocol, proper-time, rank,
or benchmark-success primitives. It does not pass promotion readiness. Target
structure can still enter through the source-only input ledger \(H\), finite
horizon choices, generator seed predicates, admissibility rules, certificate
labels, output-basis definitions, and invariant-status evidence thresholds.
Candidate reconstruction, canonical ontology edit, benchmark promotion, and
Gate Chair review remain blocked.
\end{abstract}

\section{Scope and Audit Standard}

This artifact is a draft/control output for task \texttt{RT-20260608-023}.
It does not edit canonical ontology TeX, adopt A0--A4 or selection laws as
canonical ontology, authorize candidate reconstruction, issue a Gate Chair
verdict, or reject the broader \TheoryProgram{}.

The audit asks two questions:
\begin{enumerate}
    \item Does the finite-variation repair packet directly install target
    metric, target null-cone, target coordinate, observer protocol, target
    rank, proper-time normalization, or benchmark success as a source input?
    \item Even if it avoids direct import, can its finite family generator,
    horizon bounds, admissibility predicates, certificate exclusions,
    output-basis criteria, or \(D_F\) evidence gates be selected so that
    target-like structure enters before benchmark comparison?
\end{enumerate}

The first question is a declaration screen. The second question is the
promotion-readiness screen. The word ``benchmark-blind'' is not itself a
source-forcing theorem; it must be backed by independently replayable
source-selection rules.

\section{Positive Transparency Screen}

\begin{auditfinding}[Finite-variation surfaces are explicit]
The repair packet improves the control state by exposing the choice surfaces
that the previous Refuter result identified: packet families, finite
horizons, enumerator families, certificate exclusions, output-map bases, and
status-transition gates.
\end{auditfinding}

\begin{auditfinding}[No direct target primitive is declared]
The packet does not explicitly add a Lorentzian metric, continuum topology,
target null cone, coordinate chart, observer protocol, target rank, target
proper-time normalization, or benchmark-success predicate to \(\Lang\).
\end{auditfinding}

These findings are narrow. They show that the repair packet is auditable.
They do not prove that its finite family is source-forced, target-clean, or
safe for candidate reconstruction.

\section{Input-Ledger and Packet-Family Risks}

\begin{smugglingrisk}[The source-only ledger \(H\) can encode prior target knowledge]
The packet-family generator starts from
\[
H=(R_{\mathrm{seed}},B_{\min},B_{\max},\Omega_{\mathrm{seed}},
\Rel_{\mathrm{seed}},\Gamma_{\mathrm{blind}}).
\]
If \(R_{\mathrm{seed}}\), the source closure rules, or the seed predicates
were chosen because they resemble target-local neighborhoods, target
locality enters before the generator runs. A later blinding ledger records
commitment timing, but it does not prove source necessity of the initial
ledger.
\end{smugglingrisk}

\begin{smugglingrisk}[Finite horizon selection can hide scale tuning]
The bounds \(B_{\min}\) and \(B_{\max}\) are source counts or source-order
depths. They can still be selected because the resulting finite family is
large enough to capture target-like behavior and small enough to exclude
adverse source-defined alternatives. Source-count notation does not by
itself prevent target-scale tuning.
\end{smugglingrisk}

\begin{promotionblocker}[Packet-family blocker]
\(\PackFam\) is not promotion-ready until the ledger \(H\), the horizon
bounds, and every packet exclusion are either source-forced or varied across
an admissible benchmark-blind family whose outputs and statuses are later
shown stable. The repair packet specifies this burden; it does not discharge
it.
\end{promotionblocker}

\section{Admissibility and Enumerator-Family Risks}

\begin{smugglingrisk}[Admissibility predicates can underselect source cases]
The repair packet defines \(\Ad\)-admissibility by registered source records,
finite horizons, source-operation grammars, and relabeling/refinement
symmetries. That is necessary, but the choice of which source operations,
refinements, and symmetries are admissible remains a selection channel.
Target-like topology can enter by declaring adverse source-definable
operations outside the family.
\end{smugglingrisk}

\begin{smugglingrisk}[Narrower, broader, and incomparable grammars are not fully enumerated]
The repair packet requires each \(\EnumFam_i\) to contain narrower, broader,
and incomparable source-admissible grammars. It does not yet give a
machine-checkable grammar over all such alternatives. Without that grammar,
the completeness claim can remain a naming convention rather than a
reproducible finite enumeration.
\end{smugglingrisk}

\begin{smugglingrisk}[Domain-specific families can preserve old tuning channels]
For \(D_0\), seed and refinement choices can still select target-like arena
shape. For \(D_1\), support-front choices can still encode topology. For
\(D_2\), recurrence windows and edit depths can tune rank. For \(D_3\),
quotient families can manufacture singleton spectra. For \(D_4\), transport
and cycle catalogs can encode synchronization or clock-like comparison rules.
\end{smugglingrisk}

\begin{promotionblocker}[Enumerator-family blocker]
The enumerator-family repair is transparent but not independently complete.
Every excluded source-definable grammar must be classified by source criteria
and replayable without target access before any invariant output can support
candidate reconstruction.
\end{promotionblocker}

\section{Certificate-Exclusion Risks}

\begin{smugglingrisk}[Typed labels can launder exclusions]
The repair packet improves certificate discipline by restricting labels to
\(\mathsf{duplicate}\), \(\mathsf{out\_of\_horizon}\),
\(\mathsf{source\_invalid}\), \(\mathsf{authority\_expansion}\), and
\(\mathsf{not\_computed}\). The risk remains that the label itself can carry
the tuning. An adverse case can be made harmless if it is called duplicate,
outside horizon, or source-invalid by a rule selected for target-compatible
behavior.
\end{smugglingrisk}

\begin{smugglingrisk}[Replayability is provenance, not source necessity]
Independent replay can confirm that a certificate follows the sealed rules.
It does not prove that those rules were the unique source-forced rules.
Reproducible exclusion is still an exclusion unless the source theory
justifies it without target reference.
\end{smugglingrisk}

\begin{promotionblocker}[Certificate blocker]
Certificate-exclusion evidence remains claim-bearing. The repair packet
cannot promote an invariant status until a later audit or theorem shows that
kept and omitted cases are stable under admissible certificate alternatives.
\end{promotionblocker}

\section{Output-Map and Stability-Gate Risks}

\begin{smugglingrisk}[Output-basis selection can encode the target observable]
The packet requires \(\OutFam_i\) to include favorable, adverse, and neutral
source quantities. This is a strong repair. It is still vulnerable because
the classification of a quantity as localization-relevant, adverse, neutral,
or outside the output basis can be chosen with target behavior in mind.
\end{smugglingrisk}

\begin{smugglingrisk}[Stability can be narrowed by relevance assertions]
The stability predicate permits invariant status when all allowed output
bases agree, or when non-singleton families are preserved as non-invariant.
The unresolved risk is the scope of ``allowed.'' If an adverse output is
excluded because it is declared irrelevant to localization, the repair packet
can recover apparent stability by shrinking the claim surface.
\end{smugglingrisk}

\begin{promotionblocker}[Output-map blocker]
Output-map stability is not established by preserving adverse outputs in
principle. It requires a finite, source-replayable basis generator and later
proof that favorable projections do not hide broader non-invariant families.
\end{promotionblocker}

\section{\texorpdfstring{\(D_F\)}{DF}: Status-Gate Risks}

\begin{smugglingrisk}[Evidence gates can shift the target import upward]
The five \(D_F\) gates improve status provenance. They do not remove target
import if the cited packet family, enumerator family, exclusion replay,
output-basis theorem, or audit hook already contains target-tuned choices.
The risk moves from status metadata into the evidence predicates.
\end{smugglingrisk}

\begin{smugglingrisk}[Invariant status remains a promotion-sensitive claim]
Gate F4 allows \(\mathsf{family\_valued}\) to become
\(\mathsf{invariant}\) through a source theorem or exhaustive finite-family
ledger. That transition is a scientific claim, not a bookkeeping update. A
ledger that exhausts a target-shaped finite family is not enough.
\end{smugglingrisk}

\begin{promotionblocker}[Status-gate blocker]
No \(D_F\) transition to \(\mathsf{invariant}\) is promotion-ready until the
gate evidence itself has passed target-import audit and benchmark-
independence testing. Gate F5 correctly records this audit hook, so the
repair packet blocks itself from candidate use.
\end{promotionblocker}

\section{Audit Ledger}

\begin{center}
\begin{tabular}{p{0.22\linewidth}p{0.45\linewidth}p{0.22\linewidth}}
\textbf{Surface} & \textbf{Remaining import channel} & \textbf{Audit status} \\
\hline
\(H\) and \(\PackFam\) & seed records, bounds, operation seeds, quotient seeds, and blinding ledger can encode target-like locality or scale & transparent, not promotion-ready \\
\(\EnumFam_i\) & admissibility predicates and finite grammar coverage can underselect adverse source alternatives & transparent, not promotion-ready \\
\(\Cert_i\) & duplicate, horizon, source-invalid, authority-expansion, and not-computed labels can launder exclusions & transparent, not promotion-ready \\
\(\OutFam_i\) & output-basis relevance can project away non-invariant adverse behavior & transparent, not promotion-ready \\
\(D_F\) gates & invariant-status evidence can inherit target-tuned packet, grammar, certificate, or output choices & transparent, not promotion-ready \\
\end{tabular}
\end{center}

\section{Audit Verdict}

\begin{auditverdict}[Finite-variation repair is auditable but not target-clean]
The finite-variation repair packet passes a narrow declaration audit and is
a genuine control improvement. It makes the relevant choice surfaces visible
and explicitly blocks candidate reconstruction until later audit. It does
not establish target cleanliness. Hidden target import can still enter
through the source-only input ledger, finite horizon selection, admissibility
predicates, enumerator-family coverage, certificate-exclusion labels,
output-basis relevance, and \(D_F\) invariant-status evidence.
\end{auditverdict}

This is a local control result. It does not reject the \TheoryProgram{} and
does not reject finite-variation repair as a research path. It blocks
candidate reconstruction from the present packet.

\section{Next Burden}

\begin{nextburden}[Refuter finite-variation benchmark-independence test]
The logical next role is a Refuter AgentJob that tests whether the
finite-variation repair packet is benchmark-independent under admissible
source-defined variation of \(H\), \(\PackFam\), finite horizons,
\(\EnumFam_i\), \(\Cert_i\), \(\OutFam_i\), and \(D_F\) evidence gates. The
test should ask whether localization-relevant outputs and statuses remain
stable when the repair surfaces vary by source rules alone. If outputs or
statuses vary, the result should remain a negative control result or route to
a narrower source-forcing repair packet, not to candidate reconstruction.
\end{nextburden}

Candidate Constructor, canonical ontology edit, and Gate Chair review remain
premature.

\section*{References}

Ricciardi, A. S. (2026, June 9). \emph{Localization source-basis axiom
selector-domain finite-variation repair packet: Benchmark-blind family
generators and evidence gates for D0--DF} [Unpublished manuscript]. The
Aether-Flow Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260608-022/artifacts/21\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_FINITE\_VARIATION\_REPAIR\_PACKET.tex}.

Ricciardi, A. S. (2026, June 9). \emph{Localization source-basis axiom
selector-domain finite survey protocol benchmark-independence refutation:
Invariance test for sealed packets, enumerators, certificates, output maps,
and status transitions} [Unpublished manuscript]. The Aether-Flow
Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260608-021/artifacts/20\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_FINITE\_SURVEY\_PROTOCOL\_BENCHMARK\_INDEPENDENCE\_REFUTATION.tex}.

Ricciardi, A. S. (2026, June 9). \emph{Localization source-basis axiom
selector-domain finite survey protocol smuggling audit: Target-import review
of sealed inputs, enumerators, certificates, and ledgers} [Unpublished
manuscript]. The Aether-Flow Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260608-020/artifacts/19\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_FINITE\_SURVEY\_PROTOCOL\_SMUGGLING\_AUDIT.tex}.

\end{document}
