\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.35em,itemsep=0.3em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}
\newcommand{\Lang}{\mathcal{L}_{0}}
\newcommand{\LangPlus}{\mathcal{L}_{0}^{+H}}
\newcommand{\GenH}{\mathsf{Gen}_{H}}
\newcommand{\EqSrc}{\mathsf{Eq}_{\mathrm{src}}}
\newcommand{\RetainH}{\mathsf{Retain}_{H}}
\newcommand{\NoTargetH}{\mathsf{NoTarget}_{H}}
\newcommand{\NoTargetSyn}{\mathsf{NoTarget}_{H}^{\mathrm{syn}}}
\newcommand{\Tok}{\mathsf{Tok}}
\newcommand{\SrcTok}{\mathsf{Tok}_{0}}
\newcommand{\ForbidT}{\mathsf{Forbid}_{T}}
\newcommand{\ProxyT}{\mathsf{Proxy}_{T}}
\newcommand{\TraceH}{\mathsf{Trace}_{H}}
\newcommand{\Annot}{\mathsf{Ann}}
\newcommand{\Influence}{\mathsf{Infl}}
\newcommand{\FreezeH}{\mathsf{Freeze}_{H}}
\newcommand{\Pass}{\mathsf{Pass}}
\newcommand{\Fail}{\mathsf{Fail}}
\newcommand{\Block}{\mathsf{Block}}
\newcommand{\Unres}{\mathsf{Unresolved}}

\newtheorem{definitionblock}{Definition}
\newtheorem{attempt}{Theorem attempt}
\newtheorem{lemma}{Lemma}
\newtheorem{obstruction}{Obstruction}
\newtheorem{pauserule}{Controlled-pause rule}
\newtheorem{localverdict}{Local verdict}
\newtheorem{nextburden}{Next burden}

\title{\textbf{Localization Source-Basis Axiom Selector-Domain NoTarget Source-Syntax Theorem Attempt or Controlled Pause}\\[0.35em]
\large Frozen Provenance Test for Source Tokens, Forbidden Tokens, Proxies, Annotations, and Influence}
\author{Ontology Formalizer AgentJob AJ-RT-20260613-019-001}
\date{June 13, 2026}

\begin{document}

\maketitle

\begin{abstract}
This draft/control artifact attempts the bounded \(\NoTargetSyn\) source-
syntax theorem target after the repair target passed a narrow Smuggling
Auditor screen. The theorem form is well-formed as a local burden, but it
is not discharged. The tracked record does not yet provide a complete frozen
\(\SrcTok\) inventory, an independently frozen \(\ForbidT\) inventory, a
complete \(\ProxyT\) inventory, checkable \(\Annot\) content, or complete
\(\Influence\) coverage for the trace under review. The conservative local
result is therefore \(\Block\), not \(\Pass\). \(\NoTargetH\),
\(\NoTargetSyn\), \(\EqSrc\), \(\RetainH\), and \(\GenH\) remain
undischarged. Candidate reconstruction, canonical ontology edit, benchmark
promotion, Gate Chair review, and completed-derivation language remain
blocked.
\end{abstract}

\section{Scope}

This artifact is a draft/control output for task \texttt{RT-20260613-019}.
It attempts only the source-syntax theorem target inherited from
\texttt{RT-20260613-017} and audited in \texttt{RT-20260613-018}. It does
not edit canonical ontology TeX, adopt \(\LangPlus\), authorize candidate
reconstruction, issue a Gate Chair verdict, promote benchmark status, or
claim a completed derivation.

The theorem attempt is intentionally local. It asks whether the trace under
review can receive a source-mechanical
\[
    \NoTargetSyn(\TraceH) \in \{\Pass,\Fail,\Block\}
\]
verdict using frozen provenance for \(\SrcTok\), \(\ForbidT\), \(\ProxyT\),
\(\Annot\), and \(\Influence\). It does not attempt \(\EqSrc\),
\(\RetainH\), or \(\GenH\).

\section{Frozen-Provenance Packet}

\begin{definitionblock}[Trace and freeze packet]
Let
\[
    \TraceH=(E,R,Q,A,B,S)
\]
be the source-syntax trace surface from the repair target, where \(E\) is
the finite expression set, \(R\) the relevance or admissibility-rule set,
\(Q\) the quotient or equivalence grammar, \(A\) the annotation and
provenance record set, \(B\) the blinding record set, and \(S\) the status
and retention schema.

A local theorem attempt requires a frozen provenance packet
\[
    \FreezeH =
    (\SrcTok^{*},\ForbidT^{*},\ProxyT^{*},\Annot^{*},\Influence^{*})
\]
for exactly the trace under review. The asterisk marks a fixed packet for
this theorem attempt, not canonical adoption and not reusable ontology
authority.
\end{definitionblock}

The tracked record permits the following conservative interpretation:

\begin{center}
\begin{tabular}{p{0.18\linewidth}p{0.34\linewidth}p{0.34\linewidth}}
\textbf{Surface} & \textbf{Required frozen content} & \textbf{Current local status} \\
\hline
\(\SrcTok^{*}\) & source-token inventory available to the trace & named as a required inventory, not proved complete \\
\(\ForbidT^{*}\) & target metric, proper time, locality, observer protocol, benchmark label, target-favorable rank, and benchmark-success channels & named as forbidden channels, not independently frozen before outcome inspection \\
\(\ProxyT^{*}\) & proxy-risk labels and constructs that can stand in for target success & proxy risk named, completeness not proved \\
\(\Annot^{*}\) & source basis, timing, rule scope, and dependency content for relevance and exclusion rules & annotation requirement stated, checkable content not supplied here \\
\(\Influence^{*}\) & syntactic edges into admission, equivalence, retention, ranking, status, and family selection & edge classes named, coverage not proved complete \\
\end{tabular}
\end{center}

\begin{lemma}[Well-formed source-syntax burden]
The theorem target
\[
    \NoTargetSyn(\TraceH;\FreezeH)
\]
is well-formed as a draft/control burden. The repair-target packet states
the pass, fail, and block channels, and the smuggling audit authorizes
carrying the repair target forward without treating it as theorem evidence.
\end{lemma}

\begin{proof}
The repair-target packet defines the source-syntax object
\(\TraceH=(E,R,Q,A,B,S)\), lists the required inventories
\(\SrcTok,\ForbidT,\ProxyT,\Annot,\Influence\), and requires unclassified
tokens, unannotated rules, semantic target-equivalence dependence, and
underdetermined proxy influence to return \(\Block\). The subsequent
Smuggling Auditor artifact gives the repair target a conditional local pass
only as a repair target and preserves the burdens for inventory freeze,
proxy completeness, annotation provenance, and conservative influence
coverage. Therefore the theorem target may be attempted as a local
source-syntax burden, but no proof follows merely from naming the symbols.
\end{proof}

\section{Theorem Attempt}

\begin{attempt}[NoTarget source-syntax theorem attempt]
Attempt to establish a local \(\Pass\), \(\Fail\), or \(\Block\) result for
\(\NoTargetSyn(\TraceH;\FreezeH)\) under the following rules:
\begin{enumerate}
    \item \(\Pass\) is available only if every token in \(E,R,Q,A,B,S\) is
    in \(\SrcTok^{*}\) or is introduced by explicit source-side
    declaration.
    \item \(\Fail\) follows if any token in \(\ForbidT^{*}\) occurs in
    \(E,R,Q,A,B,S\) as an admitted source primitive or rule.
    \item \(\Fail\) follows if a classified proxy in \(\ProxyT^{*}\) has a
    checkable \(\Influence^{*}\)-edge into admission, equivalence,
    retention, ranking, status, or family selection.
    \item \(\Block\) follows if \(\SrcTok^{*}\), \(\ForbidT^{*}\), or
    \(\ProxyT^{*}\) is incomplete, unfrozen, or selected after benchmark or
    target-proxy inspection.
    \item \(\Block\) follows if a relevance, exclusion, quotient,
    retention, or status rule lacks checkable \(\Annot^{*}\) content.
    \item \(\Block\) follows if \(\Influence^{*}\) coverage is incomplete
    or if deciding source admissibility requires semantic target-
    equivalence judgment.
\end{enumerate}
\end{attempt}

\section{Proof Attempt}

The proof would require five source-mechanical steps:

\begin{enumerate}
    \item prove that \(\SrcTok^{*}\) is complete for all tokens used in
    \(E,R,Q,A,B,S\);
    \item prove that \(\ForbidT^{*}\) was frozen independently of benchmark
    outcome inspection and target-proxy inspection;
    \item prove that \(\ProxyT^{*}\) contains every candidate-performance
    proxy that can affect the trace;
    \item prove that \(\Annot^{*}\) gives inspectable source basis, timing,
    rule scope, and dependency content for every relevant rule; and
    \item prove that \(\Influence^{*}\) is complete for all edges into
    admission, equivalence, retention, ranking, status, and family
    selection.
\end{enumerate}

The current tracked record states these five steps as burdens. It does not
complete them as a proof.

\begin{obstruction}[No complete source-token inventory]
The repair target requires \(\SrcTok\), but the current theorem attempt
does not possess a registered complete inventory of all tokens occurring in
\(E,R,Q,A,B,S\). Undeclared or unclassified source expressions cannot be
silently treated as allowed.
\end{obstruction}

This blocks \(\Pass\). The conservative value for an incomplete
\(\SrcTok^{*}\) inventory is \(\Block\).

\begin{obstruction}[Forbidden-token inventory not independently frozen]
\(\ForbidT\) names target metric behavior, target proper time, target
locality, target observer protocol, benchmark labels, target-favorable
ranks, and benchmark-success channels as forbidden. The tracked record does
not yet prove that this inventory was frozen before outcome inspection or
proxy inspection for the trace under review.
\end{obstruction}

This does not establish a local \(\Fail\), because the prior audit found no
direct adoption of these channels as source primitives in the repair target.
It does block \(\Pass\), because an outcome-shaped forbidden inventory can
launder target knowledge.

\begin{obstruction}[Proxy completeness not proved]
\(\ProxyT\) is named as a risk surface, but the current record does not
prove that every target-success proxy relevant to admission, equivalence,
retention, ranking, status, or family selection is classified in
\(\ProxyT^{*}\).
\end{obstruction}

An omitted proxy cannot be used as evidence of source cleanliness. Omission
or underclassification returns \(\Block\).

\begin{obstruction}[Annotation content not checkable here]
The theorem target requires annotations for relevance and exclusion rules.
The current record does not supply a complete annotation table giving source
basis, timing, rule scope, and dependency content for each relevance,
exclusion, quotient, retention, or status choice.
\end{obstruction}

A label that merely states ``source-side'' is not sufficient. Missing or
circular annotation content returns \(\Block\).

\begin{obstruction}[Influence coverage not complete]
\(\Influence\) is required to track edges into admission, equivalence,
retention, ranking, status, and family selection. The current record names
these destinations, but it does not prove that all relevant edges have been
captured.
\end{obstruction}

The theorem attempt must not use a closed-world assumption under which
unlisted influence edges are false by default. Incomplete influence coverage
returns \(\Block\).

\section{Forbidden Evidence Check}

This theorem attempt does not use target metric behavior, target proper
time, target locality, target observer protocol, target-favorable rank, or
benchmark-success predicates as source evidence. That restraint is
necessary but not sufficient. A no-direct-import screen can prevent
\(\Fail\) from direct forbidden-token occurrence while still leaving the
source-syntax theorem undischarged.

\section{Decision Ledger}

\begin{center}
\begin{tabular}{p{0.28\linewidth}p{0.42\linewidth}p{0.18\linewidth}}
\textbf{Question} & \textbf{Finding} & \textbf{Status} \\
\hline
Is the theorem form authorized? & Yes. It follows from the repair target and the conditional smuggling-audit pass. & stated \\
Is \(\SrcTok^{*}\) complete? & Not proved for all tokens in the trace. & \(\Block\) \\
Is \(\ForbidT^{*}\) independently frozen? & Not proved before outcome or proxy inspection. & \(\Block\) \\
Is \(\ProxyT^{*}\) complete? & Not proved for all target-success proxies. & \(\Block\) \\
Is \(\Annot^{*}\) checkable? & Not supplied as a complete source-provenance table. & \(\Block\) \\
Is \(\Influence^{*}\) complete? & Not proved without a closed-world assumption. & \(\Block\) \\
Can \(\NoTargetSyn\) return \(\Pass\)? & No. The required freeze and checkability burdens are not discharged. & blocked \\
Can candidate reconstruction proceed? & No. \(\NoTargetH\), \(\EqSrc\), \(\RetainH\), and \(\GenH\) remain undischarged. & blocked \\
\end{tabular}
\end{center}

\section{Local Verdict}

\begin{localverdict}[Theorem attempt reaches controlled pause]
The \(\NoTargetSyn\) theorem target is well-formed, but the local theorem is
not discharged. The current record does not prove complete frozen
\(\SrcTok^{*}\), independently frozen \(\ForbidT^{*}\), complete
\(\ProxyT^{*}\), checkable \(\Annot^{*}\), or complete
\(\Influence^{*}\). The correct local result is
\[
    \NoTargetSyn(\TraceH;\FreezeH)=\Block,
\]
not \(\Pass\).
\end{localverdict}

\begin{localverdict}[No downstream discharge follows]
This controlled pause does not prove \(\NoTargetH\) or
\(\NoTargetSyn\), does not discharge \(\EqSrc\), \(\RetainH\), or
\(\GenH\), and does not provide candidate-ready source-basis evidence.
Candidate reconstruction, canonical ontology edit, benchmark promotion,
Gate Chair review, and completed-derivation language remain blocked.
\end{localverdict}

\section{Next Burden}

\begin{nextburden}[Preserve pause unless freeze authority is explicitly supplied]
The logical next step is to preserve the \(\NoTargetSyn\) controlled pause
unless a later bounded task supplies a source-registered frozen inventory
and annotation/influence packet for the trace under review. Such a packet
would still be draft/control authority unless separately authorized. It
must not discharge \(\EqSrc\), \(\RetainH\), or \(\GenH\), and it must not
authorize candidate reconstruction, canonical ontology edit, benchmark
promotion, or Gate Chair review.
\end{nextburden}

\section*{References}

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain NoTarget source-syntax repair-target smuggling audit:
Hidden target import, proxy selection, annotation, influence, and authority
review} [Unpublished manuscript]. The Aether-Flow Interpretation of
Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-018/artifacts/34\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_SYNTAX\_REPAIR\_TARGET\_SMUGGLING\_AUDIT.tex}.

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain NoTarget source-syntax repair-target packet: Least-broad
mechanization target for target-exclusion syntax} [Unpublished manuscript].
The Aether-Flow Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-017/artifacts/33\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_SYNTAX\_REPAIR\_TARGET\_PACKET.tex}.

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain ledger-generation ontology-expansion proposal
conservativity and benchmark-independence refutation: Variation test for
provenance, admissibility, blinding, source equivalence, retention, and
target exclusion} [Unpublished manuscript]. The Aether-Flow Interpretation
of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-016/artifacts/32\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_LEDGER\_GENERATION\_ONTOLOGY\_EXPANSION\_PROPOSAL\_CONSERVATIVITY\_BENCHMARK\_INDEPENDENCE\_REFUTATION.tex}.

\end{document}
