\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.35em,itemsep=0.3em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}
\newcommand{\Lang}{\mathcal{L}_{0}}
\newcommand{\LangPlus}{\mathcal{L}_{0}^{+H}}
\newcommand{\GenH}{\mathsf{Gen}_{H}}
\newcommand{\EqSrc}{\mathsf{Eq}_{\mathrm{src}}}
\newcommand{\RetainH}{\mathsf{Retain}_{H}}
\newcommand{\NoTargetH}{\mathsf{NoTarget}_{H}}
\newcommand{\NoTargetSyn}{\mathsf{NoTarget}_{H}^{\mathrm{syn}}}
\newcommand{\Tok}{\mathsf{Tok}}
\newcommand{\SrcTok}{\mathsf{Tok}_{0}}
\newcommand{\ForbidT}{\mathsf{Forbid}_{T}}
\newcommand{\ProxyT}{\mathsf{Proxy}_{T}}
\newcommand{\TraceH}{\mathsf{Trace}_{H}}
\newcommand{\Annot}{\mathsf{Ann}}
\newcommand{\Influence}{\mathsf{Infl}}
\newcommand{\Pass}{\mathsf{Pass}}
\newcommand{\Fail}{\mathsf{Fail}}
\newcommand{\Block}{\mathsf{Block}}
\newcommand{\Risk}{\mathsf{Risk}}

\newtheorem{screen}{Audit screen}
\newtheorem{auditfinding}{Audit finding}
\newtheorem{residualrisk}{Residual risk}
\newtheorem{controlrule}{Control rule}
\newtheorem{auditverdict}{Audit verdict}
\newtheorem{nextburden}{Next burden}

\title{\textbf{Localization Source-Basis Axiom Selector-Domain NoTarget Source-Syntax Repair-Target Smuggling Audit}\\[0.35em]
\large Hidden Target Import, Proxy Selection, Annotation, Influence, and Authority Review}
\author{Smuggling Auditor AgentJob AJ-RT-20260613-018-001}
\date{June 13, 2026}

\begin{document}

\maketitle

\begin{abstract}
This draft/control audit reviews the \(\NoTargetH\) source-syntax repair
target for hidden target import, proxy-selection leakage, annotation
laundering, influence-relation laundering, and authority laundering. The
repair packet passes a narrow local audit as a repair target: it does not
directly import target metric behavior, target proper time, target observer
protocol, target locality, target-favorable rank, or benchmark success as a
source primitive, and it explicitly keeps candidate reconstruction,
canonical ontology edit, benchmark promotion, and Gate Chair review blocked.
The pass is conditional and non-promotional. \(\NoTargetSyn\), \(\SrcTok\),
\(\ForbidT\), \(\ProxyT\), \(\Annot\), and \(\Influence\) remain theorem
and mechanization burdens, not discharged source authority.
\end{abstract}

\section{Scope}

This artifact is a draft/control output for task \texttt{RT-20260613-018}.
It audits
\texttt{33\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_SYNTAX\_REPAIR\_TARGET\_PACKET.tex}.

The audit target is not whether \(\NoTargetH\) is true. The target is
narrower: whether the proposed source-syntax theorem target can be carried
forward as a repair target without laundering target knowledge or protected
authority. The audited object is the future-theorem target
\[
    \NoTargetSyn(\TraceH) \in \{\Pass,\Fail,\Block\},
\]
where the trace surface includes source tokens, forbidden target tokens,
proxy-risk constructs, provenance annotations, and a syntactic influence
relation.

\section{Audit Method}

\begin{screen}[Five-channel source-syntax smuggling screen]
The audit applies five checks:
\begin{enumerate}
    \item \textbf{Hidden target import}: whether the repair target imports
    target metric, target proper-time, target observer-protocol, target
    locality, target-favorable-rank, or benchmark-success structure as
    source syntax.
    \item \textbf{Proxy-selection leakage}: whether the proxy-risk
    inventory or proxy influence relation can be selected after seeing
    target-favorable behavior.
    \item \textbf{Annotation laundering}: whether provenance annotations
    can become labels that assert source authority without inspectable
    source provenance.
    \item \textbf{Influence-relation laundering}: whether missing or
    under-modeled influence edges can make a target proxy appear
    source-clean.
    \item \textbf{Authority laundering}: whether a local repair-target pass
    can be mistaken for canonical ontology adoption, target-exclusion proof,
    candidate readiness, or benchmark-support evidence.
\end{enumerate}
\end{screen}

\section{Hidden Target-Import Screen}

\begin{auditfinding}[No direct target primitive adoption]
The repair target lists target metric, proper time, locality, observer
protocol, benchmark label, target-favorable rank, and benchmark-success
terms only as forbidden channels. It does not define \(\NoTargetSyn\) by
successful target behavior or by reconstructing target metric structure.
\end{auditfinding}

\begin{residualrisk}[Forbidden inventories can be outcome-shaped]
\(\ForbidT\) blocks declared target tokens, but the audit does not yet prove
that the inventory was frozen before benchmark or target-proxy inspection.
If \(\ForbidT\) is chosen after observing which labels are useful for a
candidate, the inventory itself can launder target knowledge.
\end{residualrisk}

\begin{controlrule}[Inventory freeze requirement]
A future theorem attempt must treat incomplete or unfrozen \(\ForbidT\) as
\(\Block\). A \(\Pass\) result is not available unless the forbidden-token
inventory is source-registered, time-stable for the packet, and independent
of benchmark outcome inspection.
\end{controlrule}

\section{Proxy-Selection Screen}

\begin{auditfinding}[Proxy influence is correctly named as a failure surface]
The repair target does not ignore proxy risk. It requires that no
\(\ProxyT\) element have an \(\Influence\)-edge into admission,
equivalence, retention, ranking, status, or family selection.
\end{auditfinding}

\begin{residualrisk}[Proxy-risk inventory can be selection-biased]
The theorem target does not itself prove that \(\ProxyT\) is complete. A
favorable construction can omit a relevant proxy from \(\ProxyT\), then
pass the influence test because the dangerous proxy was never represented.
This is proxy-selection leakage rather than direct target import.
\end{residualrisk}

\begin{controlrule}[Proxy omissions return Block]
A future packet must make unclassified candidate-performance proxies return
\(\Block\), not \(\Pass\). The burden is source-mechanical classification of
proxy-risk constructs, not a post hoc declaration that all relevant proxies
have been listed.
\end{controlrule}

\section{Annotation-Laundering Screen}

\begin{auditfinding}[Annotations are required for relevance and exclusion]
The repair target correctly blocks unannotated relevance or exclusion rules.
This prevents an unrecorded relevance choice from passing as source syntax.
\end{auditfinding}

\begin{residualrisk}[Annotation labels can be empty authority]
\(\Annot\) can launder authority if an annotation merely states
``source-side'' without recording inspectable source basis, timing, rule
scope, and dependency surface. Such a label would preserve the appearance of
provenance while leaving the actual relevance choice ungrounded.
\end{residualrisk}

\begin{controlrule}[Annotations must carry checkable provenance]
A \(\Pass\) result requires annotations that are checkable without benchmark
outcome inspection. Missing annotation content, circular provenance, or
annotations whose relevance depends on target-equivalence judgment must
return \(\Block\).
\end{controlrule}

\section{Influence-Relation-Laundering Screen}

\begin{auditfinding}[The influence surface is broad enough to audit]
The repair target sends proxy influence into admission, equivalence,
retention, ranking, status, and family selection to \(\Fail\) or
\(\Block\). This is the correct local shape because target influence can
enter through more than direct expression tokens.
\end{auditfinding}

\begin{residualrisk}[Explicit-edge models can hide omitted influence]
An influence relation can launder target selection if only declared edges
are checked and omitted edges are treated as absent. The repair target
already states that underdetermined influence returns \(\Block\), but the
future theorem must preserve this conservative default.
\end{residualrisk}

\begin{controlrule}[No closed-world influence assumption]
The future theorem attempt must not assume that unlisted influence edges are
false unless the source syntax gives a checkable reason. Incomplete
influence coverage returns \(\Block\), not \(\Pass\).
\end{controlrule}

\section{Authority-Laundering Screen}

\begin{auditfinding}[Nonpromotion is explicit]
The repair packet states that selecting \(\NoTargetH\) as a repair target
does not prove \(\NoTargetH\), does not adopt \(\LangPlus\), does not edit
canonical ontology sources, and does not authorize candidate reconstruction,
benchmark promotion, or Gate Chair review.
\end{auditfinding}

\begin{residualrisk}[A local pass can be over-read]
Even if a later packet proves a narrow \(\NoTargetSyn\) result, that result
would be only a source-syntax guard for the trace under review. It would not
discharge \(\EqSrc\), \(\RetainH\), or \(\GenH\), and would not by itself
make a candidate reconstruction or ontology promotion admissible.
\end{residualrisk}

\section{Audit Ledger}

\begin{center}
\begin{tabular}{p{0.2\linewidth}p{0.29\linewidth}p{0.29\linewidth}p{0.12\linewidth}}
\textbf{Channel} & \textbf{Local result} & \textbf{Residual risk} & \textbf{Status} \\
\hline
Hidden target import & target channels appear as forbidden channels, not source primitives & \(\ForbidT\) may be outcome-shaped if not frozen & \(\Pass,\Risk\) \\
Proxy selection & proxy influence is a named failure surface & \(\ProxyT\) may omit useful target proxies & \(\Pass,\Block\) \\
Annotation & unannotated rules cannot pass & annotation labels can assert source authority without evidence & \(\Pass,\Block\) \\
Influence & influence reaches admission equivalence retention ranking status and family selection & missing edges can be treated as absent unless closed-world use is forbidden & \(\Pass,\Block\) \\
Authority & nonpromotion is explicit & a future local pass can be over-read as candidate readiness & \(\Pass,\Block\) \\
\end{tabular}
\end{center}

\section{Local Verdict}

\begin{auditverdict}[Conditional local pass as repair target]
The \(\NoTargetH\) source-syntax repair packet passes the narrow Smuggling
Auditor screen as a noncanonical repair target. It is acceptable to carry
forward because it makes target-token, proxy-risk, annotation, and influence
surfaces explicit, and because ambiguous or underdetermined cases are
required to return \(\Block\) rather than \(\Pass\).
\end{auditverdict}

\begin{auditverdict}[No theorem discharge follows]
The pass is not theorem evidence and not adoption authority. The audit does
not prove \(\NoTargetH\), \(\NoTargetSyn\), \(\EqSrc\), \(\RetainH\), or
\(\GenH\). Candidate reconstruction, canonical ontology edit, benchmark
promotion, Gate Chair review, and completed-derivation language remain
blocked.
\end{auditverdict}

\section{Next Burden}

\begin{nextburden}[NoTarget source-syntax theorem attempt or controlled pause]
The logical next role is an Ontology Formalizer AgentJob that attempts a
bounded \(\NoTargetSyn\) theorem packet or records controlled pause. The
packet should freeze \(\SrcTok\), \(\ForbidT\), \(\ProxyT\), \(\Annot\), and
\(\Influence\) provenance for the trace under review; preserve the rule that
unclassified tokens, unfrozen inventories, missing annotations, semantic
target-equivalence dependence, and incomplete influence coverage return
\(\Block\); and avoid any discharge of \(\EqSrc\), \(\RetainH\), or
\(\GenH\). It must not authorize candidate reconstruction, canonical
ontology edit, benchmark promotion, or Gate Chair review.
\end{nextburden}

\section*{References}

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain NoTarget source-syntax repair-target packet: Least-broad
mechanization target for target-exclusion syntax} [Unpublished manuscript].
The Aether-Flow Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-017/artifacts/33\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_SYNTAX\_REPAIR\_TARGET\_PACKET.tex}.

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain ledger-generation ontology-expansion proposal
conservativity and benchmark-independence refutation: Variation test for
provenance, admissibility, blinding, source equivalence, retention, and
target exclusion} [Unpublished manuscript]. The Aether-Flow Interpretation
of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-016/artifacts/32\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_LEDGER\_GENERATION\_ONTOLOGY\_EXPANSION\_PROPOSAL\_CONSERVATIVITY\_BENCHMARK\_INDEPENDENCE\_REFUTATION.tex}.

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain ledger-generation ontology-expansion proposal smuggling
audit: Target-import, authority-laundering, quotient-laundering, retention,
and status review} [Unpublished manuscript]. The Aether-Flow Interpretation
of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-015/artifacts/31\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_LEDGER\_GENERATION\_ONTOLOGY\_EXPANSION\_PROPOSAL\_SMUGGLING\_AUDIT.tex}.

\end{document}
