\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.35em,itemsep=0.3em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}
\newcommand{\Lang}{\mathcal{L}_{0}}
\newcommand{\Pack}{\mathcal{P}}
\newcommand{\PackFam}{\mathfrak{P}}
\newcommand{\EnumFam}{\mathfrak{E}}
\newcommand{\Cert}{\mathsf{Cert}}
\newcommand{\OutFam}{\mathfrak{O}}
\newcommand{\Ledger}{\mathsf{Ledger}}
\newcommand{\Status}{\mathsf{Status}}
\newcommand{\Ad}{\mathsf{Ad}}
\newcommand{\Blind}{\mathsf{Blind}}
\newcommand{\Stable}{\mathsf{Stable}}
\newcommand{\Force}{\mathsf{Force}}
\newcommand{\Gate}{\mathsf{Gate}}
\newcommand{\Inv}{\mathsf{Inv}}
\newcommand{\Fam}{\mathsf{Fam}}

\newtheorem{test}{Benchmark-independence test}
\newtheorem{finding}{Refutation finding}
\newtheorem{variation}{Admissible variation}
\newtheorem{blocker}{Promotion blocker}
\newtheorem{verdict}{Local verdict}
\newtheorem{nextburden}{Next burden}

\title{\textbf{Localization Source-Basis Axiom Selector-Domain Finite-Variation Benchmark-Independence Refutation}\\[0.35em]
\large Stability Test for Ledger, Packet, Horizon, Enumerator, Certificate, Output-Basis, and \(D_F\) Gate Variation}
\author{Refuter AgentJob AJ-RT-20260611-006-001}
\date{June 11, 2026}

\begin{document}

\maketitle

\begin{abstract}
This draft tests whether the selector-domain finite-variation repair packet
is benchmark-independent under admissible source-defined variation. The
result is local and negative. The packet is a genuine control improvement:
it exposes the source-only input ledger \(H\), packet-family generator,
finite horizons, enumerator families, certificate exclusions, output-basis
families, and \(D_F\) evidence gates. It also passed a narrow no-direct-
target-primitive audit. However, benchmark independence is not established.
Admissible source-side changes to ledger provenance, horizon bounds,
packet-family generation, enumerator meta-grammar, certificate labels,
output-basis scope, and status-transition evidence can still change
localization-relevant outputs or status classifications. Candidate
reconstruction, canonical ontology edit, benchmark promotion, and Gate Chair
review remain blocked.
\end{abstract}

\section{Scope and Refutation Standard}

This artifact is a draft/control output for task \texttt{RT-20260611-006}.
It does not edit canonical ontology TeX, adopt A0--A4 or selection laws as
canonical ontology, authorize candidate reconstruction, issue a Gate Chair
verdict, or reject the broader \TheoryProgram{}.

Let \(\Lang\) denote the registered source language before the A0--A4
extension sequence. The finite-variation repair packet defines a source-only
ledger
\[
H=(R_{\mathrm{seed}},B_{\min},B_{\max},\Omega_{\mathrm{seed}},
\Rel_{\mathrm{seed}},\Gamma_{\mathrm{blind}})
\]
and a finite family of repair surfaces
\[
\mathcal{V}=(\PackFam,\{\EnumFam_i\}_{i=0}^{4},
\{\Cert_i\}_{i=0}^{4},\{\OutFam_i\}_{i=0}^{4},D_F).
\]
The packet passes this Refuter test only if localization-relevant outputs
and \(D_F\) status classifications are invariant under every admissible
benchmark-blind variation of \(H\), \(\PackFam\), finite horizons,
\(\EnumFam_i\), \(\Cert_i\), \(\OutFam_i\), and the \(D_F\) evidence gates,
or if all non-invariant results are preserved as negative control outputs.

\begin{test}[Finite-variation benchmark independence]
For any two \(\Ad\)-admissible and \(\Blind\)-blind repair families
\(\mathcal{V}\) and \(\mathcal{V}'\) generated from the same registered
source vocabulary, a candidate-supporting result is allowed only if every
localization-relevant output family and every \(D_F\) status row agrees up
to declared source relabeling. If they do not agree, the correct local
status is \(\mathsf{family\_valued}\), \(\mathsf{underdetermined}\),
\(\mathsf{benchmark\_sensitive}\), or \(\mathsf{not\_computed}\), not
candidate support.
\end{test}

The term ``source-defined'' is insufficient by itself. Benchmark
independence requires source-forcing or stable preservation of the full
admissible family.

\section{Input-Ledger Variation}

\begin{finding}[Ledger provenance is not yet source-forced]
The repair packet correctly forbids direct target metrics, clocks, null
cones, observer protocols, and benchmark-success predicates in \(H\). The
remaining burden is stronger: the seed records, horizon endpoints, operation
seeds, quotient seeds, and blinding rules must be forced by source criteria
or varied across a complete source-side family.
\end{finding}

\begin{variation}[Seed-ledger alternatives]
Let \(H\) and \(H'\) differ only by source-record seeds or source closure
rules while remaining pre-benchmark and target-blind. \(H\) may select
records generated by a narrow support shell; \(H'\) may include a broader
source-accessible shell or an incomparable refinement family. Both ledgers
can be replayable from source records. They can still produce different
presentation boundaries, transition fronts, discriminator ranks, quotient
spectra, transport cycles, or status rows.
\end{variation}

\begin{blocker}[Ledger-forcing blocker]
The current packet does not supply a theorem or exhaustive finite ledger
showing that \(H\) is unique up to source relabeling, nor does it preserve
all admissible \(H'\) families as explicit negative controls. Therefore
ledger replayability is not benchmark independence.
\end{blocker}

\section{Packet-Family and Horizon Variation}

\begin{finding}[A finite family generator can remain undercomplete]
\(\PackFam\) improves the prior single-packet protocol by exposing record,
bound, operation, quotient, and blinding-ledger choices. It does not yet
prove that the finite family contains every source-admissible alternative
within the stated authority boundary.
\end{finding}

\begin{variation}[Horizon and generator variation]
Two packet-family generators may share the same source vocabulary but differ
in finite horizon endpoints, source-order depth rules, closure operators,
or refinement quotients. One generator can include a horizon that yields a
target-like invariant-looking family; another can include adverse source
alternatives that make the output family non-singleton. Both can be finite
and benchmark-blind.
\end{variation}

\begin{blocker}[Packet-family completeness not established]
No current proof shows that \(B_{\min}\), \(B_{\max}\), closure rules, and
quotient rules are source-forced rather than admissible choices. A finite
family generated by an undercomplete meta-rule is not enough to support
candidate reconstruction.
\end{blocker}

\section{Enumerator-Family Variation}

\begin{finding}[The enumerator families need a meta-grammar]
The repair packet requires narrower, broader, and incomparable grammars for
each \(D_i\). That obligation is correct. The remaining gap is a
source-forced meta-grammar for generating those grammars and proving that no
admissible adverse grammar was omitted.
\end{finding}

\begin{variation}[Domain-specific grammar alternatives]
For \(D_0\), presentation enumeration can vary by support closure and
refinement depth. For \(D_1\), transition-front enumeration can vary by exact,
prefix, or declared-overlap support. For \(D_2\), recurrence and edit-depth
windows can vary. For \(D_3\), quotient-spectrum enumeration can vary by
coarser, finer, and incomparable quotients. For \(D_4\), transport catalogs
and loop bounds can vary while remaining source-side. These variations can
change the output family without importing an explicit target primitive.
\end{variation}

\begin{blocker}[Enumerator-family stability not established]
The packet has not shown that every admissible enumerator family either
produces the same localization-relevant output or is retained as a non-
invariant family-valued result. Therefore \(\EnumFam_i\) is not yet
benchmark-independent.
\end{blocker}

\section{Certificate-Exclusion Variation}

\begin{finding}[Typed exclusions are claim-bearing]
The certificate labels
\(\mathsf{duplicate}\), \(\mathsf{out\_of\_horizon}\),
\(\mathsf{source\_invalid}\), \(\mathsf{authority\_expansion}\), and
\(\mathsf{not\_computed}\) make exclusions auditable. They do not prove that
the exclusions are invariant across admissible certificate rules.
\end{finding}

\begin{variation}[Duplicate and invalidity disagreement]
One certificate rule can label a case duplicate under a source quotient.
Another source-admissible certificate rule can retain it because it changes
a boundary, rank spectrum, transport ratio, or status row. If the retained
case changes any output basis, the protocol is certificate-sensitive even
when both rules are replayable.
\end{variation}

\begin{blocker}[Certificate-invariance blocker]
The current packet does not contain a certificate-invariance theorem proving
that every kept/omitted decision is stable across admissible certificate
families. Hash replay proves consistency with a rule, not uniqueness of the
rule.
\end{blocker}

\section{Output-Basis Variation}

\begin{finding}[Output relevance remains a selection surface]
The repair packet requires \(\OutFam_i\) to preserve favorable, adverse, and
neutral source quantities. This is stronger than the prior protocol. The
unresolved question is which source quantities are admitted into the output
basis and which are declared outside localization relevance.
\end{finding}

\begin{variation}[Broader output bases can expose non-invariance]
One output-basis generator may record only boundary and first-response-rank
data. Another may also record adverse quotient spectra, transport-cycle
ratios, or non-singleton status rows. If the narrow basis appears invariant
while the broader source-admissible basis is family-valued, the narrow
result is a projection artifact.
\end{variation}

\begin{blocker}[Output-basis generation not source-forced]
No current source theorem forces the output-basis generator or proves that
broader admissible bases are irrelevant. Candidate support cannot rest on a
favorable projection of a broader non-invariant family.
\end{blocker}

\section{\texorpdfstring{\(D_F\)}{DF}: Evidence-Gate Variation}

\begin{finding}[Status gates are scientific claims]
The \(D_F\) gates F1--F5 improve provenance. They do not make
\(\mathsf{invariant}\) a neutral bookkeeping status. Every transition to
\(\mathsf{invariant}\) depends on packet-family, enumerator-family,
certificate, output-basis, and audit predicates that themselves require
benchmark-independence support.
\end{finding}

\begin{variation}[Gate-strength variation]
One gate rule may allow \(\mathsf{family\_valued}\) to become
\(\mathsf{invariant}\) after a finite-family ledger over a selected output
basis. Another source-admissible gate rule may require stability across a
broader output-basis generator and independent certificate replay. The same
computed family can receive different statuses under these rules.
\end{variation}

\begin{blocker}[Status-transition theorem missing]
The repair packet does not yet provide a source-forced theorem for when
\(\mathsf{not\_computed}\), \(\mathsf{underdetermined}\), or
\(\mathsf{family\_valued}\) may become \(\mathsf{invariant}\). Therefore
\(D_F\) evidence gates remain a claim-bearing surface, not a promotion
license.
\end{blocker}

\section{Refutation Ledger}

\begin{center}
\begin{tabular}{p{0.22\linewidth}p{0.44\linewidth}p{0.22\linewidth}}
\textbf{Surface} & \textbf{Admissible variation} & \textbf{Local status} \\
\hline
\(H\) & seed records, closure rules, source operation seeds, quotient seeds, blinding ledger & not benchmark-independent \\
\(\PackFam\) & finite horizon endpoints, packet generator breadth, closure and quotient rules & not benchmark-independent \\
\(\EnumFam_i\) & domain-specific grammar breadth, support variants, recurrence windows, quotient and transport catalogs & not benchmark-independent \\
\(\Cert_i\) & duplicate, invalid, horizon, authority, and not-computed labels & not benchmark-independent \\
\(\OutFam_i\) & output-basis scope, adverse-output retention, relevance predicates & not benchmark-independent \\
\(D_F\) gates & evidence-threshold and status-transition rules & theorem missing \\
\end{tabular}
\end{center}

\section{Local Verdict}

\begin{verdict}[Finite-variation repair fails the current benchmark-independence test]
The finite-variation repair packet is auditable and more transparent than
the prior finite survey protocol, but it does not yet establish benchmark
independence. Admissible source-defined variation can still alter the
ledger, packet family, horizons, enumerator families, certificate
exclusions, output bases, and \(D_F\) status gates in ways that change
localization-relevant outputs or status classifications.
\end{verdict}

This is a local negative result. It does not reject the \TheoryProgram{} and
does not reject finite-variation repair as a research path. It blocks
candidate reconstruction from the present packet.

\section{Next Burden}

\begin{nextburden}[Source-forcing repair or controlled pause]
The logical next step is not Candidate Constructor and not Gate Chair review.
The next bounded task should route to an Ontology Formalizer only if the
Director determines that a narrower source-forcing packet is feasible. That
packet should state:
\begin{enumerate}
    \item a ledger-provenance criterion proving \(H\) source-forced or
    preserving all admissible \(H'\) as negative controls;
    \item horizon-universality obligations for \(B_{\min}\), \(B_{\max}\),
    and source closure depth;
    \item a source-side meta-grammar for admissible enumerator families;
    \item a certificate-invariance theorem for kept and omitted cases;
    \item an output-basis generator that retains adverse source outputs; and
    \item \(D_F\) theorem obligations for every transition to
    \(\mathsf{invariant}\).
\end{enumerate}
If those burdens cannot be stated without authority expansion or target
selection, the Director should enter a controlled pause rather than
authorize candidate reconstruction.
\end{nextburden}

\section*{References}

Ricciardi, A. S. (2026, June 10). \emph{Localization source-basis axiom
selector-domain finite-variation smuggling audit: Target-import review of
family generators, horizons, certificates, output bases, and status gates}
[Unpublished manuscript]. The Aether-Flow Interpretation of Relativity
Research Project,
\texttt{research\_control/tasks/RT-20260608-023/artifacts/22\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_FINITE\_VARIATION\_SMUGGLING\_AUDIT.tex}.

Ricciardi, A. S. (2026, June 9). \emph{Localization source-basis axiom
selector-domain finite-variation repair packet: Benchmark-blind family
generators and evidence gates for D0--DF} [Unpublished manuscript]. The
Aether-Flow Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260608-022/artifacts/21\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_FINITE\_VARIATION\_REPAIR\_PACKET.tex}.

Ricciardi, A. S. (2026, June 9). \emph{Localization source-basis axiom
selector-domain finite survey protocol benchmark-independence refutation:
Invariance test for sealed packets, enumerators, certificates, output maps,
and status transitions} [Unpublished manuscript]. The Aether-Flow
Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260608-021/artifacts/20\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_FINITE\_SURVEY\_PROTOCOL\_BENCHMARK\_INDEPENDENCE\_REFUTATION.tex}.

\end{document}
