\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{array}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.35em,itemsep=0.3em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}

\newcommand{\Lang}{\mathcal{L}_{0}}
\newcommand{\GenH}{\mathsf{Gen}_{H}}
\newcommand{\EqSrc}{\mathsf{Eq}_{\mathrm{src}}}
\newcommand{\RetainH}{\mathsf{Retain}_{H}}
\newcommand{\NoTargetH}{\mathsf{NoTarget}_{H}}
\newcommand{\NoTargetSyn}{\mathsf{NoTarget}_{H}^{\mathrm{syn}}}
\newcommand{\SrcTok}{\mathsf{Tok}_{0}}
\newcommand{\ForbidT}{\mathsf{Forbid}_{T}}
\newcommand{\ProxyT}{\mathsf{Proxy}_{T}}
\newcommand{\TraceH}{\mathsf{Trace}_{H}}
\newcommand{\Annot}{\mathsf{Ann}}
\newcommand{\Influence}{\mathsf{Infl}}
\newcommand{\FreezeH}{\mathsf{Freeze}_{H}}
\newcommand{\Pass}{\mathsf{Pass}}
\newcommand{\Fail}{\mathsf{Fail}}
\newcommand{\Block}{\mathsf{Block}}
\newcommand{\Risk}{\mathsf{Risk}}

\newtheorem{auditscreen}{Audit screen}
\newtheorem{auditfinding}{Audit finding}
\newtheorem{residualrisk}{Residual risk}
\newtheorem{controlrule}{Control rule}
\newtheorem{auditverdict}{Audit verdict}
\newtheorem{nextburden}{Next burden}

\title{\textbf{Localization Source-Basis Axiom Selector-Domain NoTarget Source-Registered Freeze Manifest Smuggling Audit}\\[0.35em]
\large Completeness, Independence, Target-Import Exclusion, Proxy, Annotation, and Influence Review}
\author{Smuggling Auditor AgentJob AJ-RT-20260613-022-001}
\date{June 13, 2026}

\begin{document}

\maketitle

\begin{abstract}
This draft/control audit reviews the source-registered freeze manifest from
task \texttt{RT-20260613-021}. The manifest passes a bounded local audit as
a future-use audit object: it supplies explicit local inventories for
\(\SrcTok\), \(\ForbidT\), \(\ProxyT\), \(\Annot\), and \(\Influence\);
records source paths and hashes; preserves conservative treatment for
unlisted or incomplete surfaces; and keeps target import, authority
laundering, and downstream promotion blocked. The pass is narrow. It does
not prove \(\NoTargetH\) or \(\NoTargetSyn\), does not discharge
\(\EqSrc\), \(\RetainH\), or \(\GenH\), and does not authorize candidate
reconstruction, canonical ontology edit, benchmark promotion, Gate Chair
review, or completed-derivation language.
\end{abstract}

\section{Scope}

This artifact is the role output for task \texttt{RT-20260613-022}. It
audits
\texttt{37\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_REGISTERED\_FREEZE\_MANIFEST.tex}.

The audit target is not whether \(\NoTargetSyn\) is true. The target is
narrower: whether the manifest can be carried forward as a frozen
draft/control input for a later theorem retry without laundering target
structure, post-outcome proxy selection, unchecked annotation authority,
missing influence edges, or protected promotion authority.

\section{Audit Method}

\begin{auditscreen}[Six-channel manifest audit]
The audit applies six checks:
\begin{enumerate}
    \item \textbf{Completeness}: whether the manifest enumerates every local
    token, forbidden channel, proxy class, annotation requirement, and
    influence edge admitted for its declared trace.
    \item \textbf{Future-use independence}: whether the manifest is frozen
    before the future theorem retry it is meant to support and whether it
    avoids retroactive proof claims for predecessor attempts.
    \item \textbf{Target-import exclusion}: whether target metric,
    target proper-time, target locality, target observer-protocol,
    benchmark-label, target-favorable-rank, or benchmark-success material is
    adopted as source syntax.
    \item \textbf{Proxy coverage}: whether proxy classes that can affect
    admission, equivalence, retention, ranking, status, or family selection
    are represented as suspect surfaces rather than silently absent.
    \item \textbf{Annotation checkability}: whether annotations carry
    checkable source-basis, timing, rule-scope, dependency, exclusion,
    proxy, influence, and manifest-use content.
    \item \textbf{Influence-edge coverage}: whether the edge ledger blocks
    closed-world inference from omitted edges and makes omissions trigger a
    new manifest requirement.
\end{enumerate}
\end{auditscreen}

\section{Completeness Screen}

\begin{auditfinding}[Finite local surfaces are explicitly listed]
The manifest supplies a finite table for \(\SrcTok^{\mathrm{RT21}}\), a
ten-channel \(\ForbidT^{\mathrm{RT21}}\) inventory, a ten-class
\(\ProxyT^{\mathrm{RT21}}\) inventory, a ten-row \(\Annot\) table, and a
fourteen-family \(\Influence\) ledger. The scope is local to the declared
\(\TraceH=(E,R,Q,A,B,S)\) trace and does not assert global source-language
completion.
\end{auditfinding}

\begin{residualrisk}[Local completeness can be over-read]
The inventory is complete only relative to the declared trace and manifest
universe. If a later theorem step needs an unlisted token, proxy, annotation
dependency, or influence edge, the correct result is a manifest-defect
finding or superseding manifest, not silent theorem completion.
\end{residualrisk}

\begin{controlrule}[Completeness is closed only by task boundary]
A later theorem retry may treat the manifest as complete only for the
listed object identifiers and declared task scope. It must not generalize
the manifest to all localization source-basis work or to canonical
ontology.
\end{controlrule}

\section{Future-Use Independence Screen}

\begin{auditfinding}[The manifest is independent relative to later use]
The manifest states its freeze timing and declares that it applies only to
future checks that cite the task and registry row. It also states that it
cannot retroactively prove that predecessor attempts already possessed an
independent pre-outcome freeze.
\end{auditfinding}

\begin{residualrisk}[Independence is not retroactive]
Because the manifest is authored after earlier controlled-pause evidence,
it cannot repair predecessor theorem attempts as if the manifest existed
before them. Its independence is prospective: it may constrain a later
\(\NoTargetSyn\) retry if that retry treats this manifest as the frozen
input.
\end{residualrisk}

\begin{controlrule}[No retroactive discharge]
Any later use must cite the manifest as future-audit evidence only.
Retrospective proof of \(\NoTargetSyn\), \(\EqSrc\), \(\RetainH\), or
\(\GenH\) from the manifest remains blocked.
\end{controlrule}

\section{Target-Import Exclusion Screen}

\begin{auditfinding}[Target channels are forbidden channels]
The manifest lists target metric import, target proper-time import, target
locality import, target observer-protocol import, benchmark-label import,
target-favorable rank import, benchmark-success evidence import,
post-outcome proxy expansion, closed-world completion, and canonical
adoption by definition as forbidden channels. They are not introduced as
source primitives.
\end{auditfinding}

\begin{residualrisk}[Forbidden naming is not absence proof]
Listing a channel as forbidden is a guard condition. It does not by itself
prove the channel is absent from every later theorem step. The later theorem
must still show absence, blocking, or source-neutrality for each relevant
step.
\end{residualrisk}

\begin{controlrule}[Forbidden channel evidence remains a theorem burden]
\(\ForbidT^{\mathrm{RT21}}\) may be used as the frozen exclusion checklist.
It may not be treated as completed target-exclusion theorem evidence.
\end{controlrule}

\section{Proxy-Coverage Screen}

\begin{auditfinding}[Proxy classes are suspect by default]
The manifest covers admission-performance, source-equivalence,
negative-control-retention, ranking, status-transition, family-selection,
notation-similarity, validation-passage, human-authorization, and
generated-derivative visibility proxies. It requires future theorem use to
show that each proxy class is absent, source-neutral, or blocked.
\end{auditfinding}

\begin{residualrisk}[Proxy coverage still needs step-level use]
The proxy table is a checklist. A theorem retry can still launder target
selection if it invokes a decision surface without mapping it to the frozen
proxy classes and influence edges.
\end{residualrisk}

\begin{controlrule}[Unmapped proxy use returns Block]
If a later proof step uses an unmapped decision proxy, the step must return
\(\Block\) or open a superseding manifest. It must not infer proxy absence
from missing table entries.
\end{controlrule}

\section{Annotation-Checkability Screen}

\begin{auditfinding}[Annotation rows carry checkable content requirements]
The manifest requires source path, object identifier, hash, admission rule,
comparison rule, retained negative controls, status basis, family-selection
rule, exclusion reason, proxy classification, influence edge content, and a
manifest-use statement that theorem discharge remains unavailable before
audit.
\end{auditfinding}

\begin{residualrisk}[Annotation rows are requirements rather than proofs]
The annotation table makes provenance checkable, but a later theorem retry
must still instantiate the rows for each proof step. A label saying
``source-side'' without path, object, hash, timing, and dependency content
would remain annotation laundering.
\end{residualrisk}

\begin{controlrule}[Empty provenance labels are not admissible]
Future use of \(\Annot^{\mathrm{RT21}}\) must preserve inspectable source
basis and timing. Empty provenance labels, circular source-basis claims, or
target-equivalence-dependent annotations return \(\Block\).
\end{controlrule}

\section{Influence-Edge Coverage Screen}

\begin{auditfinding}[The edge ledger blocks closed-world laundering]
The manifest records influence families from direct forbidden channels,
post-outcome proxy expansion, closed-world completion, canonical adoption,
and each proxy class into admission, equivalence, retention, ranking,
status, family selection, blocker, and authorization tokens. It explicitly
states that unlisted edges require a new manifest rather than default
absence.
\end{auditfinding}

\begin{residualrisk}[Coverage is finite but not global]
The edge ledger is complete only for the manifest universe. A later theorem
that needs a different decision surface cannot inherit edge absence from
this ledger.
\end{residualrisk}

\begin{controlrule}[No implicit edge absence]
Omitted influence edges cannot be interpreted as false by default. Missing
edge coverage in a later theorem retry returns \(\Block\) or requires a
new manifest.
\end{controlrule}

\section{Audit Ledger}

\begin{center}
\begin{tabular}{p{0.18\linewidth}p{0.32\linewidth}p{0.32\linewidth}p{0.10\linewidth}}
\textbf{Channel} & \textbf{Local result} & \textbf{Residual burden} & \textbf{Status} \\
\hline
Completeness & finite local inventories are supplied & local scope must not be globalized & \(\Pass,\Risk\) \\
Future-use independence & frozen for later use and nonretroactive & predecessor attempts stay paused & \(\Pass,\Risk\) \\
Target import & target channels are forbidden not adopted & step-level absence or blocking remains required & \(\Pass,\Block\) \\
Proxy coverage & proxy classes are explicit and suspect & every proof step must map proxy use & \(\Pass,\Block\) \\
Annotation & checkable annotation content is required & empty source labels still fail & \(\Pass,\Block\) \\
Influence & edge families are listed without closed-world default & new surfaces require new manifest & \(\Pass,\Block\) \\
\end{tabular}
\end{center}

\section{Local Verdict}

\begin{auditverdict}[Bounded manifest-audit pass]
The source-registered freeze manifest passes the bounded Smuggling Auditor
screen as a future-use draft/control audit object. It is admissible for a
later Director to consider a bounded \(\NoTargetSyn\) theorem retry that
cites the manifest as frozen input and preserves conservative \(\Block\)
semantics.
\end{auditverdict}

\begin{auditverdict}[No downstream discharge follows]
The audit pass is not theorem discharge and not promotion authority. It
does not prove \(\NoTargetH\) or \(\NoTargetSyn\), does not discharge
\(\EqSrc\), \(\RetainH\), or \(\GenH\), and does not authorize candidate
reconstruction, canonical ontology edit, benchmark promotion, Gate Chair
review, or completed-derivation language.
\end{auditverdict}

\section{Next Burden}

\begin{nextburden}[NoTarget theorem retry or controlled pause]
The logical next role is an Ontology Formalizer AgentJob that attempts a
bounded \(\NoTargetSyn\) theorem retry or records controlled pause using
the audited source-registered freeze manifest as the explicit frozen input.
The retry must preserve the rule that unlisted tokens, unmapped proxies,
empty annotations, implicit influence-edge absence, semantic target
dependence, or any target-channel leakage returns \(\Block\). It must not
authorize \(\EqSrc\), \(\RetainH\), \(\GenH\), candidate reconstruction,
canonical ontology edit, benchmark promotion, or Gate Chair review.
\end{nextburden}

\section*{References}

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain NoTarget source-registered freeze manifest: Complete
draft/control inventory for Tok0, ForbidT, ProxyT, Ann, and Infl}
[Unpublished manuscript]. The Aether-Flow Interpretation of Relativity
Research Project,
\texttt{research\_control/tasks/RT-20260613-021/artifacts/37\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_REGISTERED\_FREEZE\_MANIFEST.tex}.

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain NoTarget source-freeze inventory and annotation/influence
packet attempt or controlled pause: Registered-source check for the missing
NoTarget source-syntax evidence packet} [Unpublished manuscript]. The
Aether-Flow Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-020/artifacts/36\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_FREEZE\_INVENTORY\_ANNOTATION\_INFLUENCE\_PACKET\_ATTEMPT\_OR\_CONTROLLED\_PAUSE.tex}.

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain NoTarget source-syntax theorem attempt or controlled pause:
Frozen provenance test for source tokens, forbidden tokens, proxies,
annotations, and influence} [Unpublished manuscript]. The Aether-Flow
Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-019/artifacts/35\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_SYNTAX\_THEOREM\_ATTEMPT\_OR\_CONTROLLED\_PAUSE.tex}.

\end{document}
