\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.35em,itemsep=0.3em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}
\newcommand{\Lang}{\mathcal{L}_{0}}
\newcommand{\Pack}{\mathcal{P}}
\newcommand{\PackFam}{\mathfrak{P}}
\newcommand{\Enum}{\mathsf{Enum}}
\newcommand{\EnumFam}{\mathfrak{E}}
\newcommand{\Cert}{\mathsf{Cert}}
\newcommand{\Out}{\mathsf{Out}}
\newcommand{\OutFam}{\mathfrak{O}}
\newcommand{\Ledger}{\mathsf{Ledger}}
\newcommand{\Status}{\mathsf{Status}}
\newcommand{\Rel}{\mathsf{Rel}}
\newcommand{\GammaB}{\Gamma}
\newcommand{\Gate}{\mathsf{Gate}}
\newcommand{\Stable}{\mathsf{Stable}}
\newcommand{\Ad}{\mathsf{Ad}}
\newcommand{\Blind}{\mathsf{Blind}}

\newtheorem{definitionblock}{Definition}
\newtheorem{repairrule}{Repair rule}
\newtheorem{obligation}{Proof obligation}
\newtheorem{evidencegate}{Evidence gate}
\newtheorem{repairverdict}{Repair verdict}
\newtheorem{nextburden}{Next burden}

\title{\textbf{Localization Source-Basis Axiom Selector-Domain Finite-Variation Repair Packet}\\[0.35em]
\large Benchmark-Blind Family Generators and Evidence Gates for \(D_0\)--\(D_F\)}
\author{Ontology Formalizer AgentJob AJ-RT-20260608-022-001}
\date{June 9, 2026}

\begin{document}

\maketitle

\begin{abstract}
This draft responds to the finite survey protocol benchmark-independence
refutation. It proposes a finite-variation repair packet for \(D_0\)--\(D_4\)
and \(D_F\): a benchmark-blind sealed-packet family generator,
enumerator-family completeness obligations, certificate-exclusion proof
obligations, output-map stability criteria, and status-transition evidence
gates. The packet is constructive but non-promotional. It does not prove that
the repaired protocol is invariant, edit canonical ontology, authorize
candidate reconstruction, issue a Gate Chair verdict, or claim recovery of an
effective relativistic sector. Its purpose is to make the next smuggling
audit and benchmark-independence test exact.
\end{abstract}

\section{Scope and Repair Principle}

This artifact is a draft/control output for task \texttt{RT-20260608-022}.
It formalizes a repair burden named by the prior Refuter result. The result
does not make \(D_0\)--\(D_F\) successful. It defines what a repaired finite
survey protocol must state before a later role may test it.

Let \(\Lang\) denote the registered source language before the A0--A4
extension sequence. The unrepaired finite protocol fixed one sealed packet
\[
\Pack=(R,B,\Omega,\Rel,\GammaB).
\]
The repair replaces the single-packet object with a finite benchmark-blind
family
\[
\PackFam=\{\Pack_\alpha=(R_\alpha,B_\alpha,\Omega_\alpha,\Rel_\alpha,
\GammaB_\alpha):\alpha\in A\},
\]
where \(A\) is finite, source-defined, and committed before benchmark
comparison.

\begin{definitionblock}[Benchmark-blind admissibility]
A packet, enumerator, certificate, output map, or status-transition rule is
\(\Ad\)-admissible only when it is generated from registered source records,
declared finite horizon bounds, source-operation grammars, and source
relabeling/refinement symmetries. It is \(\Blind\)-blind only when its
definition, inclusion, and exclusion criteria are fixed before target
benchmark comparison and do not use target metric, target null-cone, target
coordinate, target observer protocol, target proper-time normalization,
target-favorable rank, or benchmark success.
\end{definitionblock}

\begin{repairrule}[Finite-variation repair standard]
The repaired protocol may claim local control adequacy only if it records a
finite \(\Ad\)-admissible and \(\Blind\)-blind family for each choice surface:
sealed packets, enumerator grammars, completeness certificates, output maps,
and \(D_F\) status-transition rules. If the family cannot be made finite from
source records alone, the correct outcome is a Director-controlled pause, not
candidate reconstruction.
\end{repairrule}

\section{Benchmark-Blind Packet-Family Selection}

\begin{repairrule}[Packet-family generator]
The packet-family generator \(\mathsf{Gen}_{\Pack}\) must output
\(\PackFam\) from a source-only input ledger
\[
H=(R_{\mathrm{seed}},B_{\min},B_{\max},\Omega_{\mathrm{seed}},
\Rel_{\mathrm{seed}},\Gamma_{\mathrm{blind}}).
\]
The ledger must be sealed before benchmark comparison. \(H\) may contain
source record identifiers, source-locality counts, source operation symbols,
source refinement predicates, and relabeling rules. It may not contain target
geometric, observational, clock, rank, or benchmark-success predicates.
\end{repairrule}

The generator must include the following packet-family surfaces.
\begin{enumerate}
    \item \textbf{Record-set variation.} \(R_\alpha\) ranges over the finite
    source-record subsets obtained from \(R_{\mathrm{seed}}\) by declared
    source closure and support-shell rules within the horizon.
    \item \textbf{Bound variation.} \(B_\alpha\) ranges over every source
    count or source-order depth between \(B_{\min}\) and \(B_{\max}\), unless
    an exclusion certificate proves that a bound is duplicate or syntactically
    inadmissible.
    \item \textbf{Operation-grammar variation.} \(\Omega_\alpha\) ranges over
    broader, narrower, and incomparable finite source-operation grammars
    generated by the same seed operations.
    \item \textbf{Quotient variation.} \(\Rel_\alpha\) ranges over declared
    source relabeling, refinement, coarsening, and duplicate quotients that do
    not identify localization-relevant output differences by stipulation.
    \item \textbf{Blinding-ledger variation.} \(\GammaB_\alpha\) records when
    each packet choice was fixed, which target inputs were excluded, and which
    exclusions require later audit.
\end{enumerate}

\begin{obligation}[Packet-family completeness]
For every omitted packet alternative, the repair packet must provide one of
five exclusion labels: duplicate under source relabeling, outside the finite
horizon, syntactically invalid in \(\Lang\), authority expansion required, or
not computed. ``Unhelpful for the benchmark'' and ``irrelevant to the target
candidate'' are not valid exclusion labels.
\end{obligation}

\section{Enumerator-Family Completeness}

For each \(D_i\), \(i\in\{0,1,2,3,4\}\), the repaired survey object is
\[
\mathcal{S}_i(\Pack_\alpha,\beta,\gamma,\delta)=
(\Enum_{i,\beta}(\Pack_\alpha),\Cert_{i,\gamma},
\Out_{i,\delta},\Ledger_i).
\]
Here \(\beta\) indexes finite enumerator grammars, \(\gamma\) indexes
certificate rules, and \(\delta\) indexes output-map bases.

\begin{repairrule}[Enumerator-family generator]
Each \(\EnumFam_i\) must include a source-basis grammar seed, a finite
closure horizon, expansion operators, duplicate quotients, and adverse-output
retention rules. The family must contain narrower, broader, and incomparable
source-admissible grammars whenever those grammars are generated by the same
source seed and horizon.
\end{repairrule}

\begin{obligation}[\(D_0\) presentation completeness]
\(\EnumFam_0\) must vary source-accessibility seeds, closure-word normal
forms, refinement predicates, and presentation quotients. A presentation
class may be excluded only by a source proof of duplication, horizon failure,
syntactic inadmissibility, authority expansion, or non-computation.
\end{obligation}

\begin{obligation}[\(D_1\) support-front completeness]
\(\EnumFam_1\) must vary exact support, prefix support, declared-overlap
support, support-equivalence relations, and minimality tests when each is
source-definable. Transition fronts are stable only if they survive the full
family or are preserved as family-valued outputs.
\end{obligation}

\begin{obligation}[\(D_2\) discriminator completeness]
\(\EnumFam_2\) must vary recurrence-word windows, source-local edit depths,
perturbation grammars, and discriminator closures over source counts. A
single favorable first-response rank has no standing unless the full
source-defined family is singleton or the non-singleton spectrum is preserved.
\end{obligation}

\begin{obligation}[\(D_3\) quotient-spectrum completeness]
\(\EnumFam_3\) must vary coarser, finer, and incomparable source-admissible
quotient rules. A quotient cannot be selected because it yields rank
stability. Rank spectra are stable only if the full family agrees or if the
family-valued spectrum remains the recorded result.
\end{obligation}

\begin{obligation}[\(D_4\) transport completeness]
\(\EnumFam_4\) must vary exact-support, overlap-support, cycle-catalog,
loop-bound, and transport-map grammars. Transport ratios and holonomy reports
must remain source ratios and source path data; target synchronization or
proper-time normalization remains forbidden.
\end{obligation}

\section{Certificate-Exclusion Proof Obligations}

\begin{repairrule}[Typed exclusion ledger]
Every certificate \(\Cert_{i,\gamma}\) must publish an exclusion ledger:
\[
\mathsf{Excl}_{i,\gamma}(x)\in
\{\mathsf{duplicate},\mathsf{out\_of\_horizon},
\mathsf{source\_invalid},\mathsf{authority\_expansion},
\mathsf{not\_computed}\}.
\]
The ledger must cite the source rule producing the label and must preserve
cases that change localization-relevant output as non-duplicates.
\end{repairrule}

\begin{obligation}[Certificate stability]
For each omitted object \(x\), the exclusion label must be stable across all
\(\Ad\)-admissible certificate rules in the finite family. If one admissible
certificate keeps \(x\) and another excludes \(x\), the survey result is
certificate-sensitive unless a source theorem proves the difference has no
effect on every allowed output-map basis.
\end{obligation}

\begin{obligation}[Independent replay]
Each certificate must be replayable from the sealed source ledger without
benchmark access. A reviewer must be able to recompute the exclusion labels
from \(H\), \(\Pack_\alpha\), \(\Enum_{i,\beta}\), and source grammar rules
alone. A hash is provenance evidence, not a correctness proof.
\end{obligation}

\section{Output-Map Stability Criteria}

\begin{repairrule}[Output-basis family]
For each domain \(D_i\), the repaired protocol must define a finite output
basis family \(\OutFam_i\). \(\OutFam_i\) must include favorable, adverse,
and neutral source quantities generated by the same source records. It may
not project away a non-invariant boundary, front, rank, spectrum, transport
ratio, or holonomy report in order to obtain an invariant-looking result.
\end{repairrule}

\begin{obligation}[Stability over finite variation]
The stability predicate
\[
\Stable_i(\PackFam,\EnumFam_i,\Cert_i,\OutFam_i)
\]
holds only when every benchmark-blind packet, enumerator, certificate, and
output-basis combination yields the same localization-relevant output family
up to declared source relabeling, or when the non-singleton family is kept as
\(\mathsf{family\_valued}\), \(\mathsf{underdetermined}\),
\(\mathsf{benchmark\_sensitive}\), or \(\mathsf{not\_computed}\). A favorable
projection of a broader non-invariant family is not stable.
\end{obligation}

\begin{obligation}[Adverse-output retention]
If an admissible output basis records an adverse boundary, front, rank
spectrum, cycle ratio, or status row, that output must remain in the ledger.
Later roles may prove irrelevance, but this repair packet does not permit
deletion by relevance assertion.
\end{obligation}

\section{\texorpdfstring{\(D_F\)}{DF}: Status-Transition Evidence Gates}

The repaired status ledger keeps the existing status vocabulary:
\[
\mathsf{invariant},\quad
\mathsf{family\_valued},\quad
\mathsf{underdetermined},\quad
\mathsf{benchmark\_sensitive},\quad
\mathsf{not\_computed}.
\]
It adds claim-bearing gates before any status may become
\(\mathsf{invariant}\).

\begin{evidencegate}[Gate F1: packet-family seal]
Every status row must cite the sealed packet-family ledger \(H\), the packet
family \(\PackFam\), and the packet-family completeness certificate.
\end{evidencegate}

\begin{evidencegate}[Gate F2: enumerator-family certificate]
Every status row must cite the enumerator family \(\EnumFam_i\), closure
horizon, duplicate quotient, and omitted-case ledger for the relevant domain.
\end{evidencegate}

\begin{evidencegate}[Gate F3: exclusion replay]
Every transition from \(\mathsf{not\_computed}\) or
\(\mathsf{underdetermined}\) must include a replayable certificate-exclusion
proof. If replay fails, the status remains non-invariant.
\end{evidencegate}

\begin{evidencegate}[Gate F4: output-basis stability]
Every transition from \(\mathsf{family\_valued}\) to
\(\mathsf{invariant}\) must cite a source theorem or exhaustive finite-family
ledger proving stability over \(\OutFam_i\). A narrower output projection is
not sufficient.
\end{evidencegate}

\begin{evidencegate}[Gate F5: target-exclusion audit hook]
Every invariant status must remain provisional until a Smuggling Auditor
checks the packet family, enumerator family, certificates, output maps, and
status-transition evidence for hidden target import.
\end{evidencegate}

\section{Repair Ledger}

\begin{center}
\begin{tabular}{p{0.21\linewidth}p{0.42\linewidth}p{0.25\linewidth}}
\textbf{Repair surface} & \textbf{New finite obligation} & \textbf{Current status} \\
\hline
\(\PackFam\) & benchmark-blind family generator for records, bounds, operations, quotients, and blinding ledgers & specified, not audited \\
\(\EnumFam_i\) & source-defined narrower, broader, and incomparable finite enumerator grammars for \(D_0\)--\(D_4\) & specified, not audited \\
\(\Cert_i\) & typed and replayable exclusion ledgers with stability checks & specified, not audited \\
\(\OutFam_i\) & output-basis family preserving favorable, adverse, and neutral outputs & specified, not audited \\
\(D_F\) & evidence gates F1--F5 before invariant-status transitions & specified, not audited \\
\end{tabular}
\end{center}

\section{Local Verdict and Limitations}

\begin{repairverdict}[Finite-variation repair packet specified]
This packet repairs a structural defect in the finite survey protocol by
making variation surfaces explicit. It defines the finite family generator,
enumerator-family completeness obligations, certificate-exclusion proofs,
output-map stability criteria, and \(D_F\) evidence gates needed for later
audit. It does not prove that the repaired protocol is target-clean,
benchmark-independent, or candidate-ready.
\end{repairverdict}

The result is local and non-promotional. Candidate reconstruction, canonical
ontology edit, benchmark promotion, and Gate Chair review remain blocked.

\section{Next Burden}

\begin{nextburden}[Finite-variation smuggling audit]
The logical next role is a Smuggling Auditor AgentJob that audits this
finite-variation repair packet for hidden target import. The audit should
check whether the benchmark-blind family generator, finite horizon bounds,
enumerator-family completeness predicates, certificate-exclusion labels,
output-basis stability criteria, and \(D_F\) evidence gates can still encode
target locality, topology, rank, clock, observer, or benchmark-success
information. If hidden import remains, the result should preserve a negative
control result or route to a narrower repair burden, not to candidate
reconstruction.
\end{nextburden}

\section*{References}

Ricciardi, A. S. (2026, June 9). \emph{Localization source-basis axiom
selector-domain finite survey protocol benchmark-independence refutation:
Invariance test for sealed packets, enumerators, certificates, output maps,
and status transitions} [Unpublished manuscript]. The Aether-Flow
Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260608-021/artifacts/20\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_FINITE\_SURVEY\_PROTOCOL\_BENCHMARK\_INDEPENDENCE\_REFUTATION.tex}.

Ricciardi, A. S. (2026, June 9). \emph{Localization source-basis axiom
selector-domain finite survey protocol smuggling audit: Target-import review
of sealed inputs, enumerators, certificates, and ledgers} [Unpublished
manuscript]. The Aether-Flow Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260608-020/artifacts/19\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_FINITE\_SURVEY\_PROTOCOL\_SMUGGLING\_AUDIT.tex}.

Ricciardi, A. S. (2026, June 9). \emph{Localization source-basis axiom
selector-domain finite survey protocol packet: Source-fixed enumerators and
reproducible status ledgers for D0--DF} [Unpublished manuscript]. The
Aether-Flow Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260608-019/artifacts/18\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_FINITE\_SURVEY\_PROTOCOL\_PACKET.tex}.

\end{document}
