\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{array}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.35em,itemsep=0.3em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}

\newcommand{\Lang}{\mathcal{L}_{0}}
\newcommand{\GenH}{\mathsf{Gen}_{H}}
\newcommand{\EqSrc}{\mathsf{Eq}_{\mathrm{src}}}
\newcommand{\RetainH}{\mathsf{Retain}_{H}}
\newcommand{\NoTargetH}{\mathsf{NoTarget}_{H}}
\newcommand{\NoTargetSyn}{\mathsf{NoTarget}_{H}^{\mathrm{syn}}}
\newcommand{\SrcTok}{\mathsf{Tok}_{0}}
\newcommand{\ForbidT}{\mathsf{Forbid}_{T}}
\newcommand{\ProxyT}{\mathsf{Proxy}_{T}}
\newcommand{\TraceH}{\mathsf{Trace}_{H}}
\newcommand{\Annot}{\mathsf{Ann}}
\newcommand{\Influence}{\mathsf{Infl}}
\newcommand{\FreezeH}{\mathsf{Freeze}_{H}}
\newcommand{\JudgeSyn}{\mathsf{J}_{\mathrm{syn}}}
\newcommand{\Pass}{\mathsf{Pass}}
\newcommand{\Fail}{\mathsf{Fail}}
\newcommand{\Block}{\mathsf{Block}}
\newcommand{\Risk}{\mathsf{Risk}}

\newtheorem{definitionblock}{Definition}
\newtheorem{guard}{Guard}
\newtheorem{lemma}{Lemma}
\newtheorem{theoremattempt}{Theorem retry}
\newtheorem{localverdict}{Local verdict}
\newtheorem{nextburden}{Next burden}

\title{\textbf{Localization Source-Basis Axiom Selector-Domain NoTarget Source-Syntax Theorem Retry}\\[0.35em]
\large Manifest-Bound \(\NoTargetSyn\) Adjudication After Source-Registered Freeze Audit}
\author{Ontology Formalizer AgentJob AJ-RT-20260613-023-001}
\date{June 13, 2026}

\begin{document}

\maketitle

\begin{abstract}
This draft/control artifact retries the bounded
\(\NoTargetSyn\) source-syntax theorem using the audited
source-registered freeze manifest from tasks \texttt{RT-20260613-021} and
\texttt{RT-20260613-022} as the explicit frozen input. The local result is
a manifest-bound source-syntax \(\Pass\): every admitted token surface used
by the retry is listed in the manifest; target channels occur only as
forbidden channels; proxy classes are explicit suspect surfaces; annotation
requirements are checkable; and influence edges are ledgered without
closed-world inference. The pass is narrow. It is not semantic
\(\NoTargetH\), not canonical adoption of \(\NoTargetSyn\), not
\(\EqSrc\), \(\RetainH\), or \(\GenH\) discharge, and not authority for
candidate reconstruction, canonical ontology edit, benchmark promotion,
Gate Chair review, or completed-derivation language.
\end{abstract}

\section{Scope}

This artifact is the role output for task \texttt{RT-20260613-023}. It
answers only the source-syntax adjudication question:
\[
    \JudgeSyn(\TraceH;\FreezeH^{\mathrm{reg}}_{\mathrm{RT21}})
    \in \{\Pass,\Fail,\Block\}.
\]
It does not attempt semantic target exclusion, source equivalence,
negative-control retention, generator construction, or candidate
construction. It does not edit canonical ontology TeX and does not promote a
physics claim.

\section{Frozen Input}

\begin{definitionblock}[Audited freeze manifest]
The retry uses the registered manifest
\[
    \FreezeH^{\mathrm{reg}}_{\mathrm{RT21}} =
    (\SrcTok^{\mathrm{RT21}},\ForbidT^{\mathrm{RT21}},
    \ProxyT^{\mathrm{RT21}},\Annot^{\mathrm{RT21}},
    \Influence^{\mathrm{RT21}}).
\]
The manifest is local to the declared trace
\(\TraceH=(E,R,Q,A,B,S)\). Its audited status is future-use
draft/control evidence, not retroactive proof for predecessor attempts.
\end{definitionblock}

The retry treats the following tracked sources as the frozen authority
surfaces for this local adjudication:
\begin{itemize}
    \item \texttt{research\_control/tasks/RT-20260613-022/artifacts/38\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_REGISTERED\_FREEZE\_MANIFEST\_SMUGGLING\_AUDIT.tex},
    hash \texttt{fabc42c0ff750b5c3f25beb0d0a93e2e6ec7c2513a910e457a0997872415e321}.
    \item \texttt{research\_control/tasks/RT-20260613-021/artifacts/37\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_REGISTERED\_FREEZE\_MANIFEST.tex},
    hash \texttt{b2917e3bf536ab6004edf2b9d4a4d09aec46bef10421a96f840a50519489d871}.
    \item \texttt{research\_control/tasks/RT-20260613-019/artifacts/35\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_SYNTAX\_THEOREM\_ATTEMPT\_OR\_CONTROLLED\_PAUSE.tex},
    hash \texttt{679218315cbd7a8c556e42c051528ee1b4a01ec9be9a2e0aab37b46e0d84fa1f}.
\end{itemize}

\section{Adjudication Rules}

\begin{guard}[Conservative local semantics]
The retry uses these rules:
\begin{enumerate}
    \item If a proof step needs an unlisted source token, return
    \(\Block\).
    \item If a proof step admits target metric behavior, target proper
    time, target locality, target observer protocol, benchmark label,
    target-favorable rank, benchmark-success evidence, or canonical
    adoption as a source primitive, return \(\Block\).
    \item If a proof step uses an unmapped proxy class, return \(\Block\).
    \item If a proof step relies on an empty or circular annotation, return
    \(\Block\).
    \item If a proof step infers influence-edge absence from silence,
    return \(\Block\).
    \item If a proof step requires semantic target-equivalence judgment,
    return \(\Block\).
    \item \(\Pass\) is available only when all required syntactic
    surfaces are listed, checkable, and used as guards rather than as
    semantic target evidence.
\end{enumerate}
\end{guard}

\section{Retry Lemmas}

\begin{lemma}[Source-token closure for the retry]
Every token family used by this retry is contained in the manifest's local
\(\SrcTok^{\mathrm{RT21}}\) inventory: event tokens ST-001--ST-005, rule
tokens ST-006--ST-010, registration tokens ST-011--ST-015, annotation
tokens ST-016--ST-020, blocker tokens ST-021--ST-025, and status tokens
ST-026--ST-030.
\end{lemma}

\begin{proof}
The retry uses only the event, rule, registration, annotation, blocker, and
status classes listed in the source-registered manifest. No additional
source primitive is introduced. The theorem rule for any later unlisted
token is \(\Block\), so the local proof does not rely on a closed global
language.
\end{proof}

\begin{lemma}[Forbidden channels are blockers, not source primitives]
The target channels FT-001--FT-010 occur in the retry only as forbidden
channels and blocker conditions. They are not admitted as source syntax.
\end{lemma}

\begin{proof}
The manifest lists target metric import, target proper-time import, target
locality import, target observer-protocol import, benchmark-label import,
target-favorable rank import, benchmark-success evidence import,
post-outcome proxy expansion, closed-world inference, and canonical
adoption by definition as forbidden channels. The audit found that these
are guards rather than source primitives. The retry preserves that
orientation: encountering any target-channel use returns \(\Block\), so no
target channel contributes positive source evidence.
\end{proof}

\begin{lemma}[Proxy classes are mapped as suspect surfaces]
Every proxy class available to the retry is one of PT-001--PT-010 and is
handled as a suspect surface requiring absence, source-neutrality, or
blocking.
\end{lemma}

\begin{proof}
The proxy inventory covers admission-performance, source-equivalence,
negative-control-retention, ranking, status-transition, family-selection,
notation-similarity, validation-passage, human-authorization, and
generated-derivative visibility proxies. The retry does not infer that a
proxy is harmless from its name. It treats each listed class as a possible
leakage surface and maps any unmapped proxy use to \(\Block\).
\end{proof}

\begin{lemma}[Annotations are checkable for this local use]
The annotation table AN-001--AN-010 supplies the required content classes
for source path, object identifier, hash, timing, rule scope, dependency,
exclusion, proxy classification, influence-edge content, and manifest-use
limits.
\end{lemma}

\begin{proof}
The source-registered manifest binds each annotation row to a required
content class. The retry cites tracked source paths and hashes and carries
the manifest-use statement that theorem discharge is unavailable outside
this source-syntax adjudication. Empty source-side labels, circular
annotations, or target-equivalence-dependent annotations are not admitted;
they return \(\Block\).
\end{proof}

\begin{lemma}[Influence coverage is finite without closed-world inference]
The retry uses influence families IE-001--IE-014 as the local edge ledger
and does not treat omitted edges as false by default.
\end{lemma}

\begin{proof}
The edge ledger maps direct forbidden channels, post-outcome proxy
expansion, closed-world completion, canonical adoption, and the listed proxy
classes into admission, equivalence, retention, ranking, status, family
selection, blocker, and authorization tokens. If a later step needs an
unlisted edge, the rule is \(\Block\) or a superseding manifest, not silent
absence. Therefore the retry uses finite influence coverage without hidden
closed-world completion.
\end{proof}

\section{Theorem Retry}

\begin{theoremattempt}[Manifest-bound source-syntax pass]
For the declared trace \(\TraceH=(E,R,Q,A,B,S)\) and audited freeze
manifest \(\FreezeH^{\mathrm{reg}}_{\mathrm{RT21}}\), the local
source-syntax adjudicator returns
\[
    \JudgeSyn(\TraceH;\FreezeH^{\mathrm{reg}}_{\mathrm{RT21}})
    = \Pass.
\]
\end{theoremattempt}

\begin{proof}
The pass conditions are exactly the five syntactic closure checks.
Source-token closure holds by the manifest's finite ST-001--ST-030
inventory. Forbidden target channels are represented only as FT-001--FT-010
blocker conditions, not as admitted source primitives. Proxy classes are
fully mapped for the declared trace as PT-001--PT-010 and remain suspect by
default. Annotation requirements AN-001--AN-010 provide checkable source
basis and timing fields for this local retry. Influence families IE-001--IE-014
cover the manifest universe while preserving the rule that new or omitted
edges return \(\Block\).

No step imports target metric behavior, target proper time, target locality,
target observer protocol, target-favorable rank, benchmark-success
evidence, or canonical adoption as source evidence. No step relies on an
unlisted token, unmapped proxy, empty annotation, implicit influence-edge
absence, or semantic target-equivalence judgment. Therefore the retry
passes the local source-syntax adjudicator.
\end{proof}

\section{Boundary Ledger}

\begin{center}
\begin{tabular}{p{0.24\linewidth}p{0.44\linewidth}p{0.18\linewidth}}
\textbf{Surface} & \textbf{Retry result} & \textbf{Status} \\
\hline
\(\SrcTok^{\mathrm{RT21}}\) & all admitted retry tokens are locally listed & \(\Pass\) \\
\(\ForbidT^{\mathrm{RT21}}\) & target channels are blocker conditions only & \(\Pass,\Block\) \\
\(\ProxyT^{\mathrm{RT21}}\) & proxy classes are mapped as suspect surfaces & \(\Pass,\Block\) \\
\(\Annot^{\mathrm{RT21}}\) & required annotation content is checkable for local use & \(\Pass,\Block\) \\
\(\Influence^{\mathrm{RT21}}\) & ledger covers the manifest universe without closed-world inference & \(\Pass,\Block\) \\
\(\EqSrc,\RetainH,\GenH\) & not attempted and not discharged & blocked \\
Candidate reconstruction & not authorized & blocked \\
Gate Chair review & not authorized and human-gated & blocked \\
\end{tabular}
\end{center}

\section{Local Verdict}

\begin{localverdict}[Narrow source-syntax pass]
The retried local source-syntax theorem target reaches
\[
    \NoTargetSyn(\TraceH;\FreezeH^{\mathrm{reg}}_{\mathrm{RT21}})
    = \Pass
\]
as draft/control evidence for the declared trace and manifest only.
\end{localverdict}

\begin{localverdict}[Downstream claims remain blocked]
The local pass does not prove semantic \(\NoTargetH\), does not canonically
adopt \(\NoTargetSyn\), does not discharge \(\EqSrc\), \(\RetainH\), or
\(\GenH\), and does not authorize candidate reconstruction, canonical
ontology edit, benchmark promotion, Gate Chair review, or
completed-derivation language.
\end{localverdict}

\section{Next Burden}

\begin{nextburden}[Refutation before any construction]
The logical next role is a Refuter AgentJob that stress-tests this local
\(\NoTargetSyn\) pass for benchmark independence, proxy variation, influence
ledger perturbation, annotation dependence, and source-neutrality. Candidate
Constructor remains premature until the local pass survives adversarial
variation and the separate \(\EqSrc\), \(\RetainH\), and \(\GenH\) burdens
are explicitly addressed.
\end{nextburden}

\section*{References}

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain NoTarget source-registered freeze manifest smuggling audit:
Completeness, independence, target-import exclusion, proxy, annotation, and
influence review} [Unpublished manuscript]. The Aether-Flow Interpretation
of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-022/artifacts/38\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_REGISTERED\_FREEZE\_MANIFEST\_SMUGGLING\_AUDIT.tex}.

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain NoTarget source-registered freeze manifest: Complete
draft/control inventory for Tok0, ForbidT, ProxyT, Ann, and Infl}
[Unpublished manuscript]. The Aether-Flow Interpretation of Relativity
Research Project,
\texttt{research\_control/tasks/RT-20260613-021/artifacts/37\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_REGISTERED\_FREEZE\_MANIFEST.tex}.

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain NoTarget source-syntax theorem attempt or controlled pause:
Frozen provenance test for source tokens, forbidden tokens, proxies,
annotations, and influence} [Unpublished manuscript]. The Aether-Flow
Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-019/artifacts/35\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_SYNTAX\_THEOREM\_ATTEMPT\_OR\_CONTROLLED\_PAUSE.tex}.

\end{document}
