\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{array}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.35em,itemsep=0.3em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}

\newcommand{\GenH}{\mathsf{Gen}_{H}}
\newcommand{\EqSrc}{\mathsf{Eq}_{\mathrm{src}}}
\newcommand{\RetainH}{\mathsf{Retain}_{H}}
\newcommand{\NoTargetH}{\mathsf{NoTarget}_{H}}
\newcommand{\NoTargetSyn}{\mathsf{NoTarget}_{H}^{\mathrm{syn}}}
\newcommand{\SrcTok}{\mathsf{Tok}_{0}}
\newcommand{\ForbidT}{\mathsf{Forbid}_{T}}
\newcommand{\ProxyT}{\mathsf{Proxy}_{T}}
\newcommand{\TraceH}{\mathsf{Trace}_{H}}
\newcommand{\Annot}{\mathsf{Ann}}
\newcommand{\Influence}{\mathsf{Infl}}
\newcommand{\FreezeH}{\mathsf{Freeze}_{H}}
\newcommand{\JudgeSyn}{\mathsf{J}_{\mathrm{syn}}}
\newcommand{\Pass}{\mathsf{Pass}}
\newcommand{\Fail}{\mathsf{Fail}}
\newcommand{\Block}{\mathsf{Block}}
\newcommand{\Risk}{\mathsf{Risk}}

\newtheorem{screen}{Stress screen}
\newtheorem{finding}{Finding}
\newtheorem{variant}{Variation}
\newtheorem{verdict}{Stress verdict}
\newtheorem{nextburden}{Next burden}

\title{\textbf{Localization Source-Basis Axiom Selector-Domain NoTarget Source-Syntax Benchmark-Independence and Proxy-Variation Stress Test}\\[0.35em]
\large Refuter Review of the Manifest-Bound \(\NoTargetSyn\) Source-Syntax Pass}
\author{Refuter AgentJob AJ-RT-20260613-024-001}
\date{June 14, 2026}

\begin{document}

\maketitle

\begin{abstract}
This draft/control Refuter artifact stress-tests the local
\(\NoTargetSyn\) source-syntax \(\Pass\) from task
\texttt{RT-20260613-023}. The stress test does not find a direct benchmark
label, target metric, target proper-time, target-locality,
target-observer-protocol, target-favorable-rank, or benchmark-success
primitive inside the admitted source-syntax proof path. The result survives
only source-neutral relabeling and benchmark-label erasure. It does not
survive stronger proxy omission, annotation weakening, influence-ledger
deletion, or new target-proxy perturbations as a \(\Pass\); those variants
correctly return \(\Block\) or require a superseding manifest. Therefore
the previous \(\Pass\) remains narrow, manifest-bound, and nonpromotional.
It does not discharge \(\EqSrc\), \(\RetainH\), or \(\GenH\), and does not
authorize candidate reconstruction, canonical ontology edit, benchmark
promotion, Gate Chair review, or completed-derivation language.
\end{abstract}

\section{Scope}

This artifact is the role output for task \texttt{RT-20260613-024}. It
attacks only the local result
\[
    \JudgeSyn(\TraceH;\FreezeH^{\mathrm{reg}}_{\mathrm{RT21}})=\Pass
\]
from \texttt{RT-20260613-023}. It does not issue a Gate Chair verdict, does
not edit canonical ontology, and does not attempt semantic
\(\NoTargetH\), \(\EqSrc\), \(\RetainH\), \(\GenH\), or candidate
construction.

\section{Adversarial Screens}

\begin{screen}[Five stress dimensions]
The Refuter applies five local screens:
\begin{enumerate}
    \item \textbf{Benchmark independence}: erase benchmark labels and
    benchmark-success language and check whether the proof path still uses
    only source-side manifest syntax.
    \item \textbf{Source-neutral isomorphism}: relabel source token
    identifiers while preserving token class, annotation content, and
    influence-edge incidence.
    \item \textbf{Proxy variation}: add, delete, or remap proxy classes
    relevant to admission, source equivalence, retention, ranking, status,
    family selection, validation passage, authorization, or generated
    derivative visibility.
    \item \textbf{Influence perturbation}: delete, add, or redirect edge
    families in the local \(\Influence\) ledger.
    \item \textbf{Annotation weakening}: remove source path, object
    identifier, hash, timing, rule scope, dependency, exclusion, proxy,
    influence, or manifest-use content from \(\Annot\).
\end{enumerate}
\end{screen}

\section{Benchmark-Independence Screen}

\begin{finding}[No positive benchmark primitive is used]
The theorem retry uses benchmark-related surfaces only through forbidden
channels and blocker conditions. Benchmark label import and
benchmark-success evidence import are listed in \(\ForbidT\), not admitted
into \(\SrcTok\). Erasing benchmark labels from the positive proof path
does not remove any source-token closure step.
\end{finding}

\begin{variant}[Benchmark-label erasure]
Let \(v_{\mathrm{bench}}\) erase benchmark labels, benchmark-success
phrases, and target-favorable rank labels from admitted proof steps while
leaving the blocker list intact. The local adjudicator remains
\[
    \JudgeSyn(v_{\mathrm{bench}}(\TraceH);
    \FreezeH^{\mathrm{reg}}_{\mathrm{RT21}})=\Pass
\]
only because the positive path did not use those labels.
\end{variant}

\begin{finding}[Independence remains syntactic, not semantic]
The erasure test supports only source-syntax independence from benchmark
labels. It does not prove semantic target exclusion, observational
equivalence, negative-control retention, or generator adequacy.
\end{finding}

\section{Source-Neutral Isomorphism Screen}

\begin{variant}[Source-token relabeling]
Let \(v_{\mathrm{iso}}\) replace ST, PT, AN, and IE identifiers with fresh
names while preserving class membership, annotation content, forbidden
channel status, and edge incidence. Under this isomorphism, the source
syntax proof shape is unchanged, so the manifest-bound result survives:
\[
    \JudgeSyn(v_{\mathrm{iso}}(\TraceH);
    v_{\mathrm{iso}}(\FreezeH^{\mathrm{reg}}_{\mathrm{RT21}}))=\Pass.
\]
\end{variant}

\begin{finding}[The pass is invariant only under structure-preserving
source relabeling]
This is the strongest positive stress result. The pass does not depend on
the literal token names when the manifest structure is preserved. It does
depend on the existence of the manifest fields themselves.
\end{finding}

\section{Proxy-Variation Screen}

\begin{variant}[Proxy omission]
Delete any relevant proxy class from \(\ProxyT^{\mathrm{RT21}}\), for
example validation-passage proxy PT-008 or human-authorization proxy
PT-009. A proof path that then uses the omitted decision surface lacks a
mapped proxy class. The correct adjudicator result is \(\Block\), not a
strengthened \(\Pass\).
\end{variant}

\begin{variant}[Proxy insertion]
Add a new target-success proxy \(PT\text{-}011\) that can affect admission,
source equivalence, retention, ranking, status, family selection, or
authorization. Because \(PT\text{-}011\) is not in the audited manifest,
the existing \(\Pass\) does not extend to the perturbed trace. The result
is \(\Block\) or a requirement for a superseding manifest.
\end{variant}

\begin{finding}[Proxy robustness is guard-robust, not pass-robust]
The previous theorem retry is robust in the limited sense that dangerous
proxy perturbations are blocked. It is not robust in the stronger sense
that arbitrary proxy variations preserve \(\Pass\).
\end{finding}

\section{Influence-Ledger Perturbation Screen}

\begin{variant}[Edge deletion]
Remove a ledger family such as IE-012, which links validation-passage proxy
surfaces into status and audit-required channels. The proof path can no
longer claim complete local influence coverage. The result is
\(\Block\).
\end{variant}

\begin{variant}[Edge insertion]
Insert a new edge from a target-success proxy into admission, equivalence,
retention, ranking, status, family selection, blocker, or authorization
tokens. The edge is outside the audited manifest universe. The result is
\(\Block\) or a superseding manifest requirement.
\end{variant}

\begin{finding}[No closed-world inference survives stress]
The local \(\Pass\) is acceptable only because omitted edges are not
treated as false by default. Any perturbation that needs a missing edge or
deletes required coverage blocks the pass.
\end{finding}

\section{Annotation-Dependence Screen}

\begin{variant}[Annotation weakening]
Remove path, object identifier, hash, timing, dependency, exclusion,
proxy-classification, influence-edge, or manifest-use content from an
annotation row. The annotation becomes an authority label rather than
checkable source basis. The correct adjudicator result is \(\Block\).
\end{variant}

\begin{finding}[The pass is annotation-dependent by design]
Annotation dependence is not a refutation of the local pass. It is the
control condition that prevents labels such as ``source-side'' from
laundering target-dependent relevance choices.
\end{finding}

\section{Decision Ledger}

\begin{center}
\begin{tabular}{p{0.24\linewidth}p{0.44\linewidth}p{0.18\linewidth}}
\textbf{Stress dimension} & \textbf{Refuter result} & \textbf{Status} \\
\hline
Benchmark-label erasure & positive proof path remains source-syntax only & survives narrowly \\
Source-neutral isomorphism & structure-preserving relabeling keeps result & survives narrowly \\
Proxy omission & omitted relevant proxy makes proof unmapped & \(\Block\) \\
Proxy insertion & new target-success proxy exceeds manifest & \(\Block\) \\
Influence deletion & coverage no longer complete & \(\Block\) \\
Influence insertion & new edge exceeds manifest & \(\Block\) \\
Annotation weakening & provenance becomes unchecked label & \(\Block\) \\
Semantic target comparison & outside source syntax & \(\Block\) \\
\end{tabular}
\end{center}

\section{Stress Verdict}

\begin{verdict}[Local pass survives only constrained stress]
The \(\NoTargetSyn\) source-syntax \(\Pass\) survives benchmark-label
erasure and structure-preserving source relabeling. It does not survive as
a global, monotone, or proxy-agnostic pass. Proxy omissions, new
target-success proxies, influence-ledger perturbations, weakened
annotations, and semantic target comparisons return \(\Block\) or require
a new manifest.
\end{verdict}

\begin{verdict}[No downstream discharge follows]
The stress result does not prove semantic \(\NoTargetH\), does not
canonically adopt \(\NoTargetSyn\), does not discharge \(\EqSrc\),
\(\RetainH\), or \(\GenH\), and does not authorize candidate
reconstruction, canonical ontology edit, benchmark promotion, Gate Chair
review, or completed-derivation language.
\end{verdict}

\section{Next Burden}

\begin{nextburden}[EqSrc obligation packet or controlled pause]
The logical next role is an Ontology Formalizer AgentJob that states an
\(\EqSrc\) source-equivalence obligation packet or records controlled
pause. The packet may use the stress-tested \(\NoTargetSyn\) source-syntax
guard only as draft/control input. It must not treat that guard as
\(\EqSrc\), \(\RetainH\), or \(\GenH\) discharge, and it must not
authorize candidate reconstruction, canonical ontology edit, benchmark
promotion, Gate Chair review, or completed-derivation language.
\end{nextburden}

\section*{References}

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain NoTarget source-syntax theorem retry: Manifest-bound
\(\NoTargetSyn\) adjudication after source-registered freeze audit}
[Unpublished manuscript]. The Aether-Flow Interpretation of Relativity
Research Project,
\texttt{research\_control/tasks/RT-20260613-023/artifacts/39\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_SYNTAX\_THEOREM\_RETRY.tex}.

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain NoTarget source-registered freeze manifest smuggling audit:
Completeness, independence, target-import exclusion, proxy, annotation, and
influence review} [Unpublished manuscript]. The Aether-Flow Interpretation
of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-022/artifacts/38\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_REGISTERED\_FREEZE\_MANIFEST\_SMUGGLING\_AUDIT.tex}.

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain NoTarget source-registered freeze manifest: Complete
draft/control inventory for Tok0, ForbidT, ProxyT, Ann, and Infl}
[Unpublished manuscript]. The Aether-Flow Interpretation of Relativity
Research Project,
\texttt{research\_control/tasks/RT-20260613-021/artifacts/37\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_REGISTERED\_FREEZE\_MANIFEST.tex}.

\end{document}
