\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.35em,itemsep=0.3em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}
\newcommand{\Lang}{\mathcal{L}_{0}}
\newcommand{\Pack}{\mathcal{P}}
\newcommand{\Enum}{\mathsf{Enum}}
\newcommand{\Cert}{\mathsf{Cert}}
\newcommand{\Out}{\mathsf{Out}}
\newcommand{\Ledger}{\mathsf{Ledger}}
\newcommand{\Status}{\mathsf{Status}}
\newcommand{\Dom}{\mathsf{Dom}}
\newcommand{\Inv}{\mathsf{Inv}}
\newcommand{\Rel}{\mathsf{Rel}}
\newcommand{\Pass}{\mathsf{pass}}
\newcommand{\Fail}{\mathsf{fail}}

\newtheorem{protocol}{Protocol rule}
\newtheorem{enumerator}{Enumerator}
\newtheorem{certificate}{Completeness certificate}
\newtheorem{ledger}{Ledger rule}
\newtheorem{pauserule}{Controlled-pause rule}
\newtheorem{verdict}{Local verdict}
\newtheorem{nextburden}{Next burden}

\title{\textbf{Localization Source-Basis Axiom Selector-Domain Finite Survey Protocol Packet}\\[0.35em]
\large Source-Fixed Enumerators and Reproducible Status Ledgers for \(D_0\)--\(D_F\)}
\author{Ontology Formalizer AgentJob AJ-RT-20260608-019-001}
\date{June 9, 2026}

\begin{document}

\maketitle

\begin{abstract}
This draft responds to the selector-domain benchmark-independence refutation.
It proposes a finite survey protocol for \(D_0\)--\(D_4\) and \(D_F\):
sealed source inputs, source-fixed enumerator grammars, completeness
certificates, invariance ledgers, and reproducible status transitions. The
packet is constructive but non-promotional. It does not perform the survey,
prove benchmark independence, edit canonical ontology, authorize candidate
reconstruction, issue a Gate Chair verdict, or claim recovery of an
effective relativistic sector. If any enumerator cannot be fixed from source
records alone, the protocol requires a Director-controlled pause rather than
candidate use.
\end{abstract}

\section{Scope and Protocol Standard}

This artifact is a draft/control output for task \texttt{RT-20260608-019}.
It formalizes the next evidence burden named by the prior Refuter result. It
does not make \(D_0\)--\(D_F\) successful; it defines what a reproducible
finite survey would have to contain before any later role can use
selector-domain outputs.

Let \(\Lang\) denote the registered source language before the A0--A4
extension sequence. A survey protocol is source-fixed only when its
enumerators are determined by a sealed source packet
\[
\Pack=(R,B,\Omega,\Rel,\Gamma),
\]
where \(R\) is the finite source-record set to be surveyed, \(B\) is the
declared source-locality bound, \(\Omega\) is the finite grammar of allowed
source operations, \(\Rel\) is the relabeling and refinement symmetry group
to quotient duplicates, and \(\Gamma\) is the source-only benchmark-blinding
ledger. No target metric, target null cone, target coordinate chart, target
observer protocol, target proper-time normalization, or target-favorable rank
may enter \(\Pack\).

\begin{protocol}[Sealed-input rule]
The packet \(\Pack\) must be committed before benchmark comparison. Every
enumerator, duplicate quotient, output map, and status transition must cite
only \(\Pack\) and earlier registered draft/control artifacts. Any later
change to \(R\), \(B\), \(\Omega\), \(\Rel\), or \(\Gamma\) resets the status
to \(\mathsf{benchmark\_sensitive}\) unless the change is itself audited as
benchmark-blind.
\end{protocol}

\section{Common Survey Data Model}

For each domain \(D_i\), the finite survey object has four components:
\[
\mathcal{S}_i=(\Enum_i(\Pack),\Cert_i,\Out_i,\Ledger_i).
\]
\(\Enum_i(\Pack)\) is the source-fixed finite enumerator. \(\Cert_i\) is a
machine-checkable or hand-checkable completeness certificate. \(\Out_i\)
maps each enumerated object to localization-relevant outputs. \(\Ledger_i\)
records invariance, family-valued behavior, underdetermination,
benchmark-sensitivity, or non-computation.

\begin{ledger}[Common invariance rule]
\(\Inv_i\) holds only when all enumerated objects in \(\Enum_i(\Pack)\)
produce the same \(\Out_i\) up to the declared source relabeling quotient
\(\Rel\). If outputs differ, the correct status is
\(\mathsf{family\_valued}\), \(\mathsf{underdetermined}\),
\(\mathsf{benchmark\_sensitive}\), or \(\mathsf{not\_computed}\), not
\(\mathsf{invariant}\).
\end{ledger}

\section{\texorpdfstring{\(D_0\)}{D0}: Presentation-Domain Enumerator}

\begin{enumerator}[Seeds, closures, and refinements]
\(\Enum_0(\Pack)\) enumerates triples \((U,C,\rho)\). \(U\) ranges over
source-accessibility seeds generated from \(R\) within bound \(B\). \(C\)
ranges over normal-form closure words in \(\Omega\) built from declared
source-order and source-flow operations. \(\rho\) ranges over refinement
partitions generated by source predicates in \(R\) and quotient-normalized by
\(\Rel\).
\end{enumerator}

\begin{certificate}[Presentation completeness]
\(\Cert_0\) must list the seed grammar, closure-word grammar, refinement
predicate grammar, duplicate quotient under \(\Rel\), and a terminal count
for each class. Completeness means that every source-named seed, closure,
and refinement within \(B\) has either an enumerated representative or a
recorded proof that it is duplicate, out of bound, or syntactically
inadmissible.
\end{certificate}

\(\Out_0\) records induced boundaries, adjacency-front inputs, and
response-rank inputs. \(D_0\) can be marked \(\mathsf{invariant}\) only if
these outputs agree across the enumerated quotient classes.

\section{\texorpdfstring{\(D_1\)}{D1}: Support-Equivalence Enumerator}

\begin{enumerator}[Support relations and minimality tests]
\(\Enum_1(\Pack)\) enumerates source-defined support-equivalence relations
and transition-minimality tests compatible with the \(D_0\) presentations.
The grammar may use recurrence words, source-flow labels, order support,
prefix and exact-support predicates, and finite Boolean combinations of
source predicates. It may not use target topology, geodesic adjacency,
observer protocol, or benchmark success.
\end{enumerator}

\begin{certificate}[Transition-front completeness]
\(\Cert_1\) must prove that the support predicates and minimality tests are
closed under the declared source relabelings and refinements. Each omitted
support relation must be classified as duplicate, out of grammar, or
requiring authority expansion. \(\Out_1\) records neighborhoods, transition
fronts, and minimal-step labels.
\end{certificate}

\section{\texorpdfstring{\(D_2\)}{D2}: Discriminator-Closure Enumerator}

\begin{enumerator}[Perturbations and discriminators]
\(\Enum_2(\Pack)\) enumerates source-local perturbations and discriminators
generated by recurrence words, finite transition windows, chain-internal
response distinctions, and source-local edit rules. Thresholds, windows, and
edit depths must be source counts or source-order depths declared in
\(\Pack\), not post-benchmark tuning parameters.
\end{enumerator}

\begin{certificate}[Discriminator closure]
\(\Cert_2\) must state the perturbation grammar, discriminator grammar,
closure operation, and duplicate quotient. It must also list every
first-response rank \(r_D(a,b)\) or record why the rank is not computed.
\(\Out_2\) is the full first-response-rank spectrum over the enumerated
discriminator family.
\end{certificate}

A singleton favorable rank has no special status unless it is the whole
source-fixed spectrum. A non-singleton spectrum remains a negative control
output unless a later theorem proves that the candidate claim is stable over
the full spectrum.

\section{\texorpdfstring{\(D_3\)}{D3}: Quotient and Rank-Spectrum Enumerator}

\begin{enumerator}[Response quotients]
\(\Enum_3(\Pack)\) enumerates response-word ground sets, recurrence
equivalences, source relabeling symmetries, and recombination quotients
generated from \(R\), \(B\), and \(\Omega\). The enumerator must include
coarser, finer, and incomparable source-admissible quotient rules when those
rules are generated by the sealed grammar.
\end{enumerator}

\begin{certificate}[Quotient-domain completeness]
\(\Cert_3\) must provide the quotient grammar, partition or quotient
normal-form rule, relabeling quotient, and rank-computation ledger.
\(\Out_3\) records the rank spectrum and any recombination invariants for
each quotient class.
\end{certificate}

The protocol forbids selecting one quotient because it yields a target-like
rank. Either the rank spectrum is invariant, or the family-valued spectrum is
kept as the result.

\section{\texorpdfstring{\(D_4\)}{D4}: Transport and Holonomy Enumerator}

\begin{enumerator}[Shared-support transport]
\(\Enum_4(\Pack)\) enumerates shared-support relations, stable-cycle
equivalences, and transport maps generated from source transition support
and recurrence-ratio records. The transport grammar must include exact
support, declared-overlap support, and refinement-compatible support rules
when each is source-definable from \(\Pack\).
\end{enumerator}

\begin{certificate}[Transport completeness]
\(\Cert_4\) must record the cycle catalog, loop-length bound, support
relation grammar, transport-map grammar, and relabeling quotient. \(\Out_4\)
records transported cycle ratios and holonomy reports as source ratios and
source path data only. It must not normalize them by target proper time or
target synchronization conventions.
\end{certificate}

\section{\texorpdfstring{\(D_F\)}{DF}: Status-Ledger Protocol}

\begin{ledger}[Reproducible status row]
For every \(D_i\), \(D_F\) must record:
\begin{enumerate}
    \item the sealed packet identifier for \(\Pack\);
    \item the enumerator grammar and hash;
    \item the completeness certificate status;
    \item the output map and output-family hash;
    \item target inputs excluded;
    \item benchmark-comparison time;
    \item reviewer or role responsible for the status; and
    \item the resulting status.
\end{enumerate}
\end{ledger}

\begin{ledger}[Allowed status transitions]
The allowed statuses are
\[
\mathsf{invariant},\quad
\mathsf{family\_valued},\quad
\mathsf{underdetermined},\quad
\mathsf{benchmark\_sensitive},\quad
\mathsf{not\_computed}.
\]
\(\mathsf{not\_computed}\) may become \(\mathsf{invariant}\) only after the
enumerator and completeness certificate are recorded. \(\mathsf{family\_valued}\)
may become \(\mathsf{invariant}\) only after a source-side theorem proves
that all family differences are irrelevant to the exact candidate claim.
\(\mathsf{benchmark\_sensitive}\) may not become candidate support without a
new audited sealed-input packet.
\end{ledger}

\section{Protocol Ledger}

\begin{center}
\begin{tabular}{p{0.14\linewidth}p{0.38\linewidth}p{0.37\linewidth}}
\textbf{Domain} & \textbf{Finite enumerator} & \textbf{Required certificate} \\
\hline
\(D_0\) & seeds, closures, refinements & grammar completeness and presentation quotient \\
\(D_1\) & support equivalences, minimality tests & transition-front domain completeness \\
\(D_2\) & perturbations, discriminators & closure of source-local discriminator family \\
\(D_3\) & response quotients, recombination rules & quotient-domain and rank-ledger completeness \\
\(D_4\) & support transports, stable cycles & cycle catalog and transport-map completeness \\
\(D_F\) & status rows and transitions & reproducible status provenance \\
\end{tabular}
\end{center}

\section{Controlled Pause Conditions}

\begin{pauserule}[Authority-expansion stop]
If any \(D_i\) requires an unbounded predicate grammar, an unstated source
operation, a target-derived locality criterion, a target-derived clock
normalization, or a survey class too broad to enumerate under the sealed
packet \(\Pack\), the correct result is not candidate reconstruction. The
correct result is a Director-controlled pause or a narrower follow-up task
that explicitly requests authority to define the missing source-side bound.
\end{pauserule}

\section{Local Verdict}

\begin{verdict}[Finite survey protocol proposed but not yet audited]
This packet supplies the formal shape of a finite selector-domain survey. It
does not show that the enumerators are already complete, that invariance
holds, or that localization-relevant outputs are benchmark-independent. It
therefore preserves the prior blockers: no canonical ontology edit, no
candidate reconstruction, no benchmark promotion, and no Gate Chair review.
\end{verdict}

\section{Next Burden}

\begin{nextburden}[Audit the finite survey protocol]
The logical next role is a Smuggling Auditor AgentJob. It should test whether
the enumerator grammars, completeness certificates, invariance ledgers, and
status-transition rules hide target locality, topology, observer protocol,
rank, clock normalization, or benchmark-tuned branch selection. Candidate
Constructor, canonical ontology edit, and Gate Chair review remain
premature.
\end{nextburden}

\section*{References}

Ricciardi, A. S. (2026, June 9). \emph{Localization source-basis axiom
selector-domain benchmark-independence refutation: Invariance test for
repaired survey domains D0--DF} [Unpublished manuscript]. The Aether-Flow
Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260608-018/artifacts/17\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_BENCHMARK\_INDEPENDENCE\_REFUTATION.tex}.

Ricciardi, A. S. (2026, June 9). \emph{Localization source-basis axiom
selector-domain smuggling audit: Target-import review of survey domains and
invariance criteria for D0--DF} [Unpublished manuscript]. The Aether-Flow
Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260608-017/artifacts/16\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_SMUGGLING\_AUDIT.tex}.

Ricciardi, A. S. (2026, June 9). \emph{Localization source-basis axiom
selector-domain repair packet: Survey domains, invariance criteria, and
negative-result status rules for S0--SF} [Unpublished manuscript]. The
Aether-Flow Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260608-016/artifacts/15\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_REPAIR\_PACKET.tex}.

\end{document}
