\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.35em,itemsep=0.3em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}
\newcommand{\Sub}{\mathcal{A}}
\newcommand{\PhiFlow}{\Phi_{\lambda}}
\newcommand{\Data}{\mathcal{D}_{\mathrm{loc}}}
\newcommand{\Map}{\mathcal{L}_{\mathrm{loc}}}
\newcommand{\Constraints}{\mathcal{C}_{\mathrm{loc}}}
\newcommand{\Front}{\mathcal{F}}
\newcommand{\Order}{\mathcal{S}}
\newcommand{\Obs}{\mathcal{O}}

\newtheorem{definition}{Definition}
\newtheorem{proposal}{Candidate proposal}
\newtheorem{constraint}{Constraint}
\newtheorem{test}{Required test}
\newtheorem{verdict}{Candidate status}

\title{\textbf{Localization Candidate Packet}\\[0.35em]
\large A Source-Side Observer-Localization Map for Gate 0 Review}
\author{Candidate Constructor AgentJob AJ-RT-20260608-003-001}
\date{June 8, 2026}

\begin{document}

\maketitle

\begin{abstract}
This draft constructs one bounded candidate localization packet for the
\TheoryProgram{}. It responds to the Gate 0 burden ledger by specifying
additional source-side data, a conditional localization map, anti-smuggling
constraints, and failure tests. The packet is intentionally modest: it is a
candidate for the missing observer-localization object, not a derivation of the
effective Einsteinian sector. Its main result is that the next scientific
obstruction can be made precise. A source front relation and a clock-order
functional must jointly induce an observer-accessible conformal structure
without importing a target metric, and then an independent scale calibration
must be supplied before metric recovery can even be tested.
\end{abstract}

\section{Scope and Authority}

This artifact is a draft/control output for task \texttt{RT-20260608-003}. It
reads the Gate 0 ontology formalization and the registered ontology package, but
it does not edit canonical ontology TeX. Its purpose is to create one concrete
candidate packet for later Smuggling Auditor and Refuter review.

The current exact-closure benchmark remains external to the source packet. The
candidate below may use that benchmark only as a recovery target and failure
test. It may not assume the Lorentzian metric \(g_{\mu\nu}\), the
Einstein-Hilbert action, the Einstein equations, or universal matter coupling as
source primitives.

\section{Gate 0 Input}

The Gate 0 ledger fixed the allowed primitive reservoir as
\[
(\Sub,\PhiFlow,\iota_s,\Order),
\]
with optional future variables \(\chi\). It also fixed the missing object: a
localization map from source structure to observer-accessible metric, clocks,
spatial slices, and lightlike propagation. The present packet therefore defines
\[
\Data=(\Sub,\PhiFlow,\chi_{\mathrm{loc}},\Map,\Constraints)
\]
as a candidate, not as a theorem.

\section{Additional Source Data}

\begin{definition}[Observer chain]
An observer chain \(\Gamma\subset\Sub\) is a localized ordered sequence of
source states that remains coherently identifiable under \(\PhiFlow\) over the
candidate regime. Coherence means that neighboring stages of the chain preserve
a stable internal transition pattern; it does not mean that \(\Gamma\) is
already a GR worldline.
\end{definition}

\begin{definition}[Clock-order functional]
For each admissible observer chain \(\Gamma\), the source clock-order functional
is
\[
\Order_{\Gamma}:\Gamma\rightarrow\mathbb{R},
\]
with \(\Order_{\Gamma}\) monotone along the chain. A later model may calibrate
this order by repeatable internal cycles, but this packet does not identify
\(\Order_{\Gamma}\) with target proper time.
\end{definition}

\begin{definition}[Source front relation]
The source front relation
\[
\Front\subset\Sub\times\Sub
\]
records which source transitions can first influence which other source
transitions under \(\PhiFlow\). It is not a metric null cone. It is primitive
only as an influence-front relation induced by ordered substrate behavior.
\end{definition}

\begin{definition}[Coincidence response map]
The coincidence response map
\[
\kappa_{\Gamma}:\Sub\supset U_{\Gamma}\rightarrow
(\Order_{\Gamma},r^1_{\Gamma},r^2_{\Gamma},r^3_{\Gamma})
\]
assigns local observer labels to source events inside an observer-accessible
domain \(U_{\Gamma}\). The three response labels \(r^i_{\Gamma}\) are defined
operationally by repeated interactions between \(\Gamma\) and nearby source
fronts, not by an imported spatial metric.
\end{definition}

The candidate additional variables are therefore
\[
\chi_{\mathrm{loc}}
=
(\Gamma,\Order_{\Gamma},\Front,\kappa_{\Gamma},\alpha_{\Gamma}),
\]
where \(\alpha_{\Gamma}\) is a clock-scale calibration factor fixed only by
stable source cycles.

\section{Localization Map}

\begin{proposal}[Candidate localization map]
The localization map \(\Map\) acts in four stages:
\begin{enumerate}
    \item Select coherent observer chains \(\Gamma\) from stable patterns of
    \(\PhiFlow\).
    \item Use \(\Order_{\Gamma}\) to assign local clock order along each chain.
    \item Use \(\Front\) and \(\kappa_{\Gamma}\) to assign observer-accessible
    coincidence labels in \(U_{\Gamma}\).
    \item If the image of \(\Front\) under \(\kappa_{\Gamma}\) is a smooth
    double-front structure with one invariant local signal speed, reconstruct a
    candidate conformal class \([g_{\mathrm{eff}}]\). If stable clock-scale
    data \(\alpha_{\Gamma}\) exist, attempt to lift \([g_{\mathrm{eff}}]\) to a
    metric candidate \(g_{\mathrm{eff}}\).
\end{enumerate}
\end{proposal}

The logical order matters. The front relation supplies the candidate causal
structure; clock-scale calibration supplies the conformal scale. Neither is
allowed to be copied from the exact-closure metric. If the front relation does
not define a smooth Lorentz-signature cone after localization, the candidate
fails before any metric comparison begins.

\section{Anti-Smuggling Constraints}

\begin{constraint}[No metric primitive]
\(\Front\) must be specified without using \(g_{\mu\nu}\), \(ds^2\), target
null cones, or GR observer congruences as primitives.
\end{constraint}

\begin{constraint}[No action import]
The packet does not include the Einstein-Hilbert action, Einstein tensor, or
universal target matter coupling in \(\chi_{\mathrm{loc}}\).
\end{constraint}

\begin{constraint}[Dimensional discipline]
The packet must state dimensions before a later derivational claim is tested.
At this stage \(\lambda\) and \(\Order_{\Gamma}\) may be order parameters;
\(\alpha_{\Gamma}\) carries the burden of turning repeatable source cycles into
clock units. The source front relation must specify whether its limiting speed
is dimensional, emergent from calibration, or dimensionless before comparison
with \(c\).
\end{constraint}

\begin{constraint}[Gauge and redundancy]
Relabelings of \(\Sub\), \(\lambda\), and observer response coordinates must be
treated as source-side redundancy unless they change observable coincidence
data. Target diffeomorphism symmetry is a recovery target, not a primitive
assumption.
\end{constraint}

\section{Required Tests}

\begin{test}[Local cone test]
In each observer domain \(U_{\Gamma}\), the localized image of \(\Front\) must
be tested for a smooth double-front structure. If this fails, the packet cannot
support relativistic observer localization.
\end{test}

\begin{test}[Clock-scale test]
The candidate must show that \(\Order_{\Gamma}\) and \(\alpha_{\Gamma}\) define
stable clock readings independent of arbitrary relabeling of the source order.
Without this, only a conformal structure can be attempted.
\end{test}

\begin{test}[Preferred-frame leakage test]
The packet must check whether \(\Gamma\) or \(\Front\) introduces observable
preferred-frame effects outside the exact-closure benchmark. Any such leakage is
a failure unless it is confined to a clearly non-operational redundancy.
\end{test}

\begin{test}[Benchmark recovery test]
Only after the prior tests pass may the candidate be compared with the
exact-closure target. The comparison must ask whether the localized
\((g_{\mathrm{eff}},\psi_{\mathrm{eff}})\) can support the same one-metric
matter law and dynamical limit. This packet does not supply that proof.
\end{test}

\section{Status and Next Role}

\begin{verdict}[Conditionally admissible, underdetermined]
The packet is admissible as a candidate because it identifies a concrete
source-side localization object:
\[
\Data
=
(\Sub,\PhiFlow,\Gamma,\Order_{\Gamma},\Front,\kappa_{\Gamma},
\alpha_{\Gamma},\Map,\Constraints).
\]
It is underdetermined because \(\Front\), the observer-chain selection rule, and
the clock-scale calibration are not yet derived from a source action or unique
substrate law.
\end{verdict}

The substantive gain is not a promoted physics claim. It is a sharper
obstruction. The project no longer lacks only a vague bridge from ontology to
observers; it now has a candidate bridge with named failure points. The first
logical review is a Smuggling Auditor pass focused on whether \(\Front\),
\(\kappa_{\Gamma}\), or \(\alpha_{\Gamma}\) secretly imports the target metric
or its operational clock/null structure.

\section*{References}

Ricciardi, A. S. (2026, June 8). \emph{Gate 0 ontology formalization: Source
primitives, forbidden imports, and localization burden} [Unpublished
manuscript]. The Aether-Flow Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260608-002/artifacts/01\_GATE0\_ONTOLOGY\_FORMALIZATION.tex}.

Ricciardi, A. S. (2026, June 8). \emph{The Aether-flow Interpretation of
Relativity: Foundations} [Unpublished manuscript]. The Aether-Flow
Interpretation of Relativity Research Project,
\texttt{ontology/tex/aether\_flow\_foundations.tex}.

Ricciardi, A. S. (2026, June 8). \emph{The Aether-flow Interpretation of
Relativity: Exact-closure note} [Unpublished manuscript]. The Aether-Flow
Interpretation of Relativity Research Project,
\texttt{ontology/tex/aether\_flow\_exact\_closure\_note.tex}.

\end{document}
