\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{array}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.35em,itemsep=0.3em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}

\newcommand{\Obj}{\mathsf{Obj}_{0}^{\mathrm{iso}}}
\newcommand{\Inv}{\mathsf{Inv}_{0}^{\mathrm{iso}}}
\newcommand{\Cmp}{\mathsf{Cmp}_{0}^{\mathrm{iso}}}
\newcommand{\EqSrc}{\mathsf{Eq}_{\mathrm{src}}}
\newcommand{\EqIso}{\mathsf{Eq}_{\mathrm{src}}^{\mathrm{iso}}}
\newcommand{\GenH}{\mathsf{Gen}_{H}}
\newcommand{\RetainH}{\mathsf{Retain}_{H}}
\newcommand{\NoTargetH}{\mathsf{NoTarget}_{H}}
\newcommand{\NoTargetSyn}{\mathsf{NoTarget}_{H}^{\mathrm{syn}}}
\newcommand{\SrcTok}{\mathsf{Tok}_{0}}
\newcommand{\ForbidT}{\mathsf{Forbid}_{T}}
\newcommand{\ProxyT}{\mathsf{Proxy}_{T}}
\newcommand{\TraceH}{\mathsf{Trace}_{H}}
\newcommand{\Annot}{\mathsf{Ann}}
\newcommand{\Influence}{\mathsf{Infl}}
\newcommand{\FreezeH}{\mathsf{Freeze}_{H}}
\newcommand{\Pass}{\mathsf{Pass}}
\newcommand{\Block}{\mathsf{Block}}
\newcommand{\Risk}{\mathsf{Risk}}

\newtheorem{auditscreen}{Audit screen}
\newtheorem{auditfinding}{Audit finding}
\newtheorem{residualrisk}{Residual risk}
\newtheorem{controlrule}{Control rule}
\newtheorem{auditverdict}{Audit verdict}
\newtheorem{nextburden}{Next burden}

\title{\textbf{Localization Source-Basis Axiom Selector-Domain EqSrc Source-Relabeling Isomorphism Datum Smuggling Audit}\\[0.35em]
\large Target-Import Review of the Local \(\EqIso\) Witness Packet}
\author{Smuggling Auditor AgentJob AJ-RT-20260613-027-001}
\date{June 14, 2026}

\begin{document}

\maketitle

\begin{abstract}
This draft/control artifact audits the local \(\EqIso\) datum supplied in
task \texttt{RT-20260613-026}. The audit conditionally passes the datum
only as a source-relabeling isomorphism witness: the positive case uses
bijective preservation of source token class, forbidden-channel
orientation, proxy mapping, annotation content, influence-edge incidence,
and manifest-bound adjudicator shape. Annotation weakening and unmapped
proxy controls still return \(\Block\). The result does not discharge
general \(\EqSrc\), \(\RetainH\), or \(\GenH\); it does not prove semantic
\(\NoTargetH\); and it does not authorize candidate reconstruction,
canonical ontology edit, benchmark promotion, Gate Chair review, or
completed-derivation language.
\end{abstract}

\section{Scope}

This artifact is the role output for task \texttt{RT-20260613-027}. It
audits only the local datum
\[
    \mathcal{E}_{0}^{\mathrm{iso}}=(\Obj,\Inv,\Cmp,\Annot,\Influence)
\]
from \texttt{RT-20260613-026}. The audit target is not whether
\(\EqSrc\) is globally established. The target is narrower: whether the
local source-relabeling positive case launders target success through
notation, manifest choice, proxy selection, annotation preservation,
influence-edge selection, or authority labels.

\section{Audit Method}

\begin{auditscreen}[Six-channel target-import audit]
The Smuggling Auditor applies six checks:
\begin{enumerate}
    \item \textbf{Notation laundering}: whether the relabeling witness uses
    symbol similarity or target-favorable naming as positive evidence.
    \item \textbf{Manifest selection}: whether the positive pair is chosen
    by target success or by the registered source-manifest structure.
    \item \textbf{Proxy selection}: whether source-equivalence,
    notation-similarity, validation, authorization, generated-visibility,
    ranking, or status proxies select the positive result.
    \item \textbf{Annotation preservation}: whether annotation content is
    inspectable source evidence or merely an authority label.
    \item \textbf{Influence-edge selection}: whether omitted or favorable
    influence edges are used as silent absence evidence.
    \item \textbf{Authority labels}: whether local validation, registry
    entry, role identity, or human-readable derivative visibility is treated
    as scientific promotion.
\end{enumerate}
\end{auditscreen}

\section{Notation and Relabeling}

\begin{auditfinding}[The positive case is source-structural, not nominal]
The positive witness pair \((X_{0},X_{1})\) is admitted only when the map
from \(X_{0}\) to \(X_{1}\) is bijective on the ST, PT, AN, and IE
identifier classes and preserves token class, annotation content,
forbidden-channel orientation, proxy class, and influence-edge incidence.
The datum therefore does not use literal token names as positive evidence.
\end{auditfinding}

\begin{residualrisk}[Relabeling is close to identity]
The witness pair is intentionally weak: \(X_{1}\) is a
structure-preserving relabeling of \(X_{0}\), not an independently
generated source object family. A pass for this pair cannot be promoted
into general \(\EqSrc\) without additional source-object variation,
equivalence-relation properties, and negative-control retention evidence.
\end{residualrisk}

\begin{controlrule}[Do not over-read \(\EqIso\)]
The notation \(\EqIso\) must remain the local relabeling-isomorphism
judgment. It is not canonical \(\EqSrc\), not a quotient construction, and
not evidence for \(\RetainH\) or \(\GenH\).
\end{controlrule}

\section{Manifest Selection}

\begin{auditfinding}[The manifest lineage selects a local source object]
The datum is tied to the registered \(\NoTargetSyn\) freeze-manifest and
stress-test lineage. The positive pair is selected because the stress test
already recorded survival under structure-preserving source-neutral
relabeling, not because a target metric, target proper time, target
locality, target observer protocol, benchmark rank, or benchmark-success
surface improves.
\end{auditfinding}

\begin{residualrisk}[Manifest scope is local]
The manifest is local to the declared trace and its registered source
surfaces. New trace families, new object domains, omitted proxies,
additional influence surfaces, or altered annotations require a new datum
or a \(\Block\) result.
\end{residualrisk}

\begin{controlrule}[No manifest globalization]
The manifest may be used only as the local source universe for this audit.
It cannot be generalized into canonical source-language completeness or
candidate-ready source-basis evidence.
\end{controlrule}

\section{Proxy and Comparison Selection}

\begin{auditfinding}[Proxy surfaces are guards rather than evidence]
The datum explicitly carries PT-002 source-equivalence proxy risk, PT-007
notation-similarity proxy risk, validation-passage, authorization, and
generated-visibility proxy surfaces as suspect guard classes. The positive
rule does not ask whether a target result succeeds; it asks whether the
source-manifest structure is preserved by a bijection.
\end{auditfinding}

\begin{auditfinding}[Negative controls remain active]
The annotation-weakening and unmapped-proxy variants return \(\Block\).
This prevents the comparison rule from collapsing into a label agreement
test or a target-success proxy.
\end{auditfinding}

\begin{residualrisk}[Proxy coverage is not general retention]
The two negative controls are sufficient for the local audit but not for
general source-equivalence use. Broader \(\EqSrc\) would require systematic
negative-control retention across object families and comparison classes.
\end{residualrisk}

\section{Annotation and Influence}

\begin{auditfinding}[Annotation preservation is checkable locally]
The datum preserves source path, object identifier, hash, timing, rule
scope, dependency, exclusion, proxy classification, influence-edge content,
and manifest-use limits through AN-001, AN-002, AN-008, AN-009, and
AN-010. Annotation preservation is therefore an inspectable local condition,
not a bare authority label.
\end{auditfinding}

\begin{auditfinding}[Influence edges are blocker guards]
IE-006, IE-011, IE-012, IE-013, and IE-014 appear as guard edges for
source-equivalence proxy risk, notation-similarity risk,
validation-passage proxy surfaces, human-authorization proxy surfaces, and
generated-derivative visibility proxy surfaces. They are not positive
equivalence evidence.
\end{auditfinding}

\begin{residualrisk}[No closed-world inference is still required]
The audit pass depends on preserving the rule that omitted influence edges
do not count as absent by default. Any later proof step that needs an
unlisted edge must return \(\Block\) or open a superseding manifest.
\end{residualrisk}

\section{Authority Labels}

\begin{auditfinding}[Registry and role labels do not promote the datum]
The datum is registered as a draft/control artifact. Registration,
validation passage, wiki generation, role identity, or handoff language is
not treated as canonical ontology authority or benchmark promotion.
\end{auditfinding}

\begin{controlrule}[Promotion remains blocked]
Any later use that treats this audit pass as canonical ontology,
candidate-ready evidence, Gate Chair eligibility, or completed derivation
must return \(\Block\) at the research-control boundary.
\end{controlrule}

\section{Audit Ledger}

\begin{center}
\begin{tabular}{p{0.22\linewidth}p{0.42\linewidth}p{0.18\linewidth}}
\textbf{Screen} & \textbf{Local audit result} & \textbf{Status} \\
\hline
Notation & bijective source-token relabeling preserves structure & \(\Pass\) local \\
Manifest choice & selected by registered source-manifest lineage & \(\Pass,\Risk\) \\
Proxy selection & proxy classes remain suspect guards & \(\Pass,\Block\) \\
Negative controls & annotation weakening and unmapped proxy block & \(\Pass,\Block\) \\
Annotation & required content is preserved and inspectable & \(\Pass,\Block\) \\
Influence & edges are guard surfaces without closed-world inference & \(\Pass,\Block\) \\
Authority labels & registry role and validation status are not promotion & \(\Pass\) local \\
General \(\EqSrc\) & not established by relabeling witness & blocked \\
\(\RetainH,\GenH\) & not attempted & blocked \\
Candidate reconstruction & not authorized & blocked \\
\end{tabular}
\end{center}

\section{Audit Verdict}

\begin{auditverdict}[Local conditional pass]
The local \(\EqIso\) datum conditionally passes this smuggling audit:
\[
    \Cmp(X_{0},X_{1};\Inv)=\EqIso(X_{0},X_{1})
\]
does not appear to import target metric behavior, target proper time,
target locality, target observer protocol, target-favorable rank,
benchmark-success evidence, or authority status as positive source
evidence. The pass is limited to the manifest-bound source-relabeling
pair.
\end{auditverdict}

\begin{auditverdict}[Downstream discharge remains blocked]
The audit does not discharge general \(\EqSrc\), \(\RetainH\), or
\(\GenH\). It does not prove semantic \(\NoTargetH\), does not canonically
adopt \(\NoTargetSyn\), and does not authorize candidate reconstruction,
canonical ontology edit, benchmark promotion, Gate Chair review, or
completed-derivation language.
\end{auditverdict}

\section{Next Burden}

\begin{nextburden}[Refuter stress before equivalence generalization]
The logical next role is a Refuter AgentJob that stress-tests this local
\(\EqIso\) datum under nontrivial source-object variation and
equivalence-relation generalization pressure. The stress test should ask
whether any broader use survives non-identity object variation, expanded
negative controls, invariant weakening, influence perturbation, and
quotient or relation-property checks. Until that succeeds, broader
\(\EqSrc\), \(\RetainH\), \(\GenH\), candidate reconstruction, canonical
ontology edit, benchmark promotion, Gate Chair review, and
completed-derivation language remain blocked.
\end{nextburden}

\section*{References}

Ricciardi, A. S. (2026, June 14). \emph{Localization source-basis axiom
selector-domain EqSrc source-relabeling isomorphism datum: Bounded
Ontology Formalizer evidence-supply packet for the manifest-bound
\(\NoTargetSyn\) trace} [Unpublished manuscript]. The Aether-Flow
Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-026/artifacts/42\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_EQSRC\_SOURCE\_RELABELING\_ISOMORPHISM\_DATUM.tex}.

Ricciardi, A. S. (2026, June 14). \emph{Localization source-basis axiom
selector-domain EqSrc source-equivalence obligation packet or controlled
pause: Ontology Formalizer review after the stress-tested
\(\NoTargetSyn\) source-syntax guard} [Unpublished manuscript]. The
Aether-Flow Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-025/artifacts/41\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_EQSRC\_SOURCE\_EQUIVALENCE\_OBLIGATION\_PACKET\_OR\_CONTROLLED\_PAUSE.tex}.

Ricciardi, A. S. (2026, June 14). \emph{Localization source-basis axiom
selector-domain NoTarget source-syntax benchmark-independence and
proxy-variation stress test: Refuter review of the manifest-bound
\(\NoTargetSyn\) source-syntax pass} [Unpublished manuscript]. The
Aether-Flow Interpretation of Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-024/artifacts/40\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_NO\_TARGET\_SOURCE\_SYNTAX\_BENCHMARK\_INDEPENDENCE\_PROXY\_VARIATION\_STRESS\_TEST.tex}.

\end{document}
