\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage{amsmath,amssymb,amsfonts,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}

\geometry{margin=1in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue, citecolor=black}
\setlist[enumerate]{topsep=0.35em,itemsep=0.3em}
\setlist[itemize]{topsep=0.3em,itemsep=0.25em}

\newcommand{\Aether}{\AE{}ther}
\newcommand{\Aflow}{\AE{}ther-flow}
\newcommand{\TheoryProgram}{\Aether{} / \Aflow{} framework}
\newcommand{\Lang}{\mathcal{L}_{0}}
\newcommand{\LangPlus}{\mathcal{L}_{0}^{+H}}
\newcommand{\LedgerFam}{\mathfrak{H}}
\newcommand{\PiH}{\Pi_H}
\newcommand{\Ad}{\mathsf{Ad}}
\newcommand{\Blind}{\mathsf{Blind}}
\newcommand{\GenH}{\mathsf{Gen}_{H}}
\newcommand{\EnvH}{\mathsf{Env}_{H}}
\newcommand{\EqSrc}{\mathsf{Eq}_{\mathrm{src}}}
\newcommand{\Retain}{\mathsf{Retain}}
\newcommand{\NoTarget}{\mathsf{NoTarget}}
\newcommand{\Audit}{\mathsf{Audit}}
\newcommand{\Thm}{\mathsf{Thm}}
\newcommand{\Block}{\mathsf{Block}}

\newtheorem{proposal}{Proposal}
\newtheorem{definitionblock}{Definition}
\newtheorem{axiomcandidate}{Candidate rule}
\newtheorem{burden}{Theorem burden}
\newtheorem{guard}{Guard}
\newtheorem{verdict}{Local verdict}
\newtheorem{nextburden}{Next burden}

\title{\textbf{Localization Source-Basis Axiom Selector-Domain Ledger-Generation Ontology-Expansion Proposal}\\[0.35em]
\large Noncanonical Source-Language Authority Candidate for Family-First Ledger Provenance}
\author{Ontology Formalizer AgentJob AJ-RT-20260613-010-001}
\date{June 13, 2026}

\begin{document}

\maketitle

\begin{abstract}
This draft/control artifact proposes, but does not adopt, a source-language
ontology expansion for the missing ledger-generation authority identified by
the controlled-pause result for
\(\mathsf{LedgerProv}_{\Lang}(\Pi_H,H,\LedgerFam)\). The proposal is a
family-first ledger-generation envelope \(\EnvH\) in a candidate extension
\(\LangPlus\). Its first output is an admissible ledger family
\(\LedgerFam_{\PiH}\), not a distinguished candidate-supporting ledger.
Uniqueness, complete retention, and any later candidate support remain
separate theorem burdens. This artifact does not edit canonical ontology
TeX, does not adopt new axioms, does not authorize candidate reconstruction,
does not promote benchmark status, and does not request Gate Chair review.
\end{abstract}

\section{Scope}

This artifact is a draft/control output for task \texttt{RT-20260613-010}.
It responds to explicit human authorization to propose an ontology expansion
for missing source-language ledger-generation authority.

The proposal is intentionally weaker than adoption. It defines a candidate
source-language extension that can be audited and refuted before any
canonical ontology change is considered. The existing controlled pause
therefore remains active for candidate-support purposes.

\section{Problem Statement}

The prior ledger-provenance theorem attempt established a precise blocker:
the current registered source language \(\Lang\) does not prove a
source-forced ledger generator \(\mathsf{Force}_H\), uniqueness of \(H\) up
to declared source relabeling, or complete retention of all non-equivalent
admissible ledgers. A direct rule selecting \(H\) would be unsafe because it
could smuggle benchmark-favorable structure into source language.

\begin{proposal}[Minimal expansion target]
The proposed expansion target is not a rule selecting \(H\). It is a
source-language envelope
\[
    \EnvH:\Pi_H\longmapsto \LedgerFam_{\PiH}
\]
that generates a complete family of admissible ledgers from source
provenance records. A later theorem may identify uniqueness, equivalence
classes, or retained negative controls. Until that theorem exists,
\(\LedgerFam_{\PiH}\) remains family-valued draft/control evidence only.
\end{proposal}

\section{Candidate Extension}

Let \(\LangPlus\) be a proposed noncanonical extension of \(\Lang\). It adds
only source-side vocabulary for ledger generation and retention:
\[
\LangPlus =
\Lang \cup
\{\Ad_H,\Blind_H,\GenH,\EqSrc,\Retain_H,\NoTarget_H,\Audit_H\}.
\]
The intended meanings are:
\begin{itemize}
    \item \(\Ad_H(\Pi,H')\): \(H'\) is source-admissible from provenance
    packet \(\Pi\).
    \item \(\Blind_H(\Pi,H')\): \(H'\) is constructed without benchmark
    outcome inspection.
    \item \(\GenH(\Pi)\): the generated family of all ledgers satisfying
    source admissibility and blinding constraints.
    \item \(\EqSrc(H',H'')\): declared source relabeling equivalence.
    \item \(\Retain_H(H')\): non-equivalent ledgers remain retained as
    negative-control alternatives.
    \item \(\NoTarget_H\): a syntactic exclusion predicate for target metric,
    target locality, target observer protocol, target proper-time
    normalization, target-favorable rank, and benchmark-success predicates.
    \item \(\Audit_H\): a required audit marker before any canonical use.
\end{itemize}

\section{Candidate Rules}

\begin{axiomcandidate}[Source provenance packet]
The only admissible input to \(\GenH\) is
\[
\Pi_H=(\mathcal{R}_{0},\mathcal{C}_{0},\mathcal{O}_{0},
\mathcal{Q}_{0},\mathcal{B}_{0}),
\]
where the components are source records, source closure rules, source
operation seeds, source quotient seeds, and pre-benchmark blinding records.
No target-effective predicate may appear in \(\Pi_H\).
\end{axiomcandidate}

\begin{axiomcandidate}[Family-first generation]
\[
\GenH(\Pi_H)=
\{H' : \Ad_H(\Pi_H,H')\wedge \Blind_H(\Pi_H,H')\wedge \NoTarget_H(\Pi_H,H')\}.
\]
This rule generates a family. It does not select a preferred ledger and does
not convert a generated ledger into candidate support.
\end{axiomcandidate}

\begin{axiomcandidate}[Equivalence after generation]
Source equivalence is evaluated only after the family has been generated:
\[
H'\sim_{\mathrm{src}}H'' \quad \text{iff} \quad \EqSrc(H',H'').
\]
An equivalence theorem may later collapse the family, but equivalence cannot
be assumed by definition.
\end{axiomcandidate}

\begin{axiomcandidate}[Complete retention]
For every generated ledger \(H'\), either \(H'\) is source-equivalent to a
declared representative or it is retained:
\[
H'\in\GenH(\Pi_H)
\Rightarrow
\bigl(\exists H''\,\EqSrc(H',H'')\bigr)
\vee
\Retain_H(H').
\]
Retained ledgers may be used as negative controls, not candidate-supporting
evidence.
\end{axiomcandidate}

\begin{axiomcandidate}[Audit before adoption]
No rule in \(\LangPlus\) may be promoted to canonical ontology authority
without a separate smuggling audit and later human-gated ontology action.
\[
\LangPlus \Rightarrow \Audit_H \wedge \Block(\text{canonical adoption}).
\]
\end{axiomcandidate}

\section{Theorem Burdens Created by the Proposal}

\begin{burden}[Conservative extension burden]
Prove that \(\LangPlus\) is conservative over \(\Lang\) for all
pre-existing source claims. In particular, adding \(\GenH\) must not imply
candidate reconstruction, benchmark success, target metric recovery, or any
new canonical ontology claim.
\end{burden}

\begin{burden}[Completeness burden]
Prove that \(\GenH(\Pi_H)\) contains every ledger that is admissible,
blind, and target-clean under the declared source provenance packet. Without
this theorem, the generated family remains incomplete.
\end{burden}

\begin{burden}[Equivalence burden]
Prove that \(\EqSrc\) is an equivalence relation and that each quotient
class corresponds only to declared source relabeling. If a quotient erases
adverse source behavior, the proposal fails audit.
\end{burden}

\begin{burden}[Retention burden]
Prove that every non-equivalent generated ledger is retained with its
outputs and statuses, and that no retained alternative is projected away
for candidate convenience.
\end{burden}

\begin{burden}[Target-exclusion burden]
Prove that \(\NoTarget_H\) mechanically excludes target metric behavior,
target locality, target observer protocol, target proper-time
normalization, target-favorable rank, benchmark success, and downstream
candidate performance.
\end{burden}

\section{Guard Conditions}

\begin{guard}[No uniqueness by syntax]
The proposal forbids defining \(H\) as the unique output of \(\GenH\). Any
uniqueness claim must be a theorem over the generated family, not a
definition of the generator.
\end{guard}

\begin{guard}[No candidate-support shortcut]
The generated family \(\LedgerFam_{\PiH}\) is not a candidate packet.
Candidate Constructor remains blocked until a later audited theorem package
discharges generation, uniqueness or complete retention, and all dependent
surfaces required by the control state.
\end{guard}

\begin{guard}[No canonical ontology edit]
This artifact is not a patch to canonical ontology TeX. It supplies a
candidate expansion target for audit. Adoption requires a separate
human-gated ontology action.
\end{guard}

\section{Local Verdict}

\begin{verdict}
The proposal supplies a coherent next object for scrutiny: a source-only,
family-first ledger-generation envelope. It does not solve ledger
provenance. It converts the previous missing-authority blocker into an
auditable expansion proposal with explicit theorem burdens and guard
conditions.
\end{verdict}

\begin{nextburden}
Run a Smuggling Auditor audit of \(\LangPlus\), \(\EnvH\), \(\GenH\),
\(\EqSrc\), \(\Retain_H\), and \(\NoTarget_H\). The audit should test for
hidden target import, authority laundering, quotient laundering, retention
failure, and status laundering. Candidate reconstruction, canonical
ontology edit, benchmark promotion, and Gate Chair review remain blocked.
\end{nextburden}

\section{References}

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain ledger-provenance theorem attempt or controlled pause:
Single-surface current-language test for Pi\_H, H, and admissible ledger
retention} [Unpublished manuscript]. The Aether-Flow Interpretation of
Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-009/artifacts/29\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_LEDGER\_PROVENANCE\_THEOREM\_ATTEMPT\_OR\_CONTROLLED\_PAUSE.tex}.

Ricciardi, A. S. (2026, June 13). \emph{Localization source-basis axiom
selector-domain source-forcing discharge protocol: Current-language
obligations, negative controls, protected expansions, and unresolved
statuses} [Unpublished manuscript]. The Aether-Flow Interpretation of
Relativity Research Project,
\texttt{research\_control/tasks/RT-20260613-006/artifacts/26\_LOCALIZATION\_SOURCE\_BASIS\_AXIOM\_SELECTOR\_DOMAIN\_SOURCE\_FORCING\_DISCHARGE\_PROTOCOL.tex}.

\end{document}
